---
title: "Cultural Normativity Index: Study 2"
format: 
  pdf:
    prefer-html: true
    mainfont: Times
    mainfontoptions: 
       - Numbers=OldStyle
       - Ligatures=TeX
    monofontoptions: Scale=0.9 
    fontsize: 11.2pt
    code-block-font-size: 9pt
    toc: true
    number-sections: true
    number-depth: 3
    section-divs: true
    toc-depth: 3
    secnumdepth: 3
    lof: true
    lot: true
    execute:
       warning: false
       message: false
       timeout: 300
    code-block-wrap: true
    code-overflow: wrap
    include-in-header: 
      text: |
         \usepackage[T1]{fontenc}
    documentclass: article
    geometry: margin=1in
    papersize: letter
    keep-tex: true
    crossref:
      fig-prefix: "Figure"
      lof-title: "List of Figures"
    extra_dependencies: ["pdflscape", "booktabs", "longtable"]
editor: source
---

```{r eval=FALSE, echo=FALSE}
#Notes: For code chunks that have `DONT-RUN` in their labels involve computations that take longer, require parallel processing or higher GPUs. These will be typically followed by code for loading objects that have been saved after running these chunks. 
```

# Data set up

The data, originally in the .sav format, is identified by labels for each set of items. Scale scores for individual and community (here, country) level are computed for each measure.

```{r Libraries}

options(timeout = max(300, getOption("timeout")))
#if (!require("pacman")) install.packages("pacman")
#pacman::p_install() #for installing libraries 

pacman::p_load(tidyverse, dplyr, rio, expss, scales, glue,
               rlang, kableExtra, stringr, tibble, psych, here, tools,
               haven, parallel, tictoc, papaja, #wrangling and setup
               patchwork,gridExtra, ggplot2, grid, ggtext, #plots
               lme4, lmerTest, broom.mixed, tidyr, #modeling - mlm
               emmeans, marginaleffects, modelsummary, 
               pbkrtest, car #model estimates
               )  
 
options(modelsummary_get = "easystats")
```

```{r data2-wrangle}
#| cache: true

#---Data import
all_data2 <- import(here::here("data", "SWV2012.sav"), setclass = "tibble")

#get all factor levels
all_data2_factor_cols <- read_sav(here::here("data", "SWV2012.sav"))%>%
  mutate(across(c("Nation33", "Language", "D_SX",  "D_FH",  "D_ME",  "D_FE"), haven::as_factor)) %>% 
  select("Nation33", "Language", "D_SX",  "D_FH",  "D_ME",  "D_FE") %>% 
  tibble()

#attr(all_data2_spss$Nation33, "labels") 


#---Globe items rename

#Study1 pattern of Globe names, only pattern is similar the names here don't exactly map on the same variables as in Study 1
s1_GlobeNames <- c("g1igc1", "g1un1", "g1pf1", "g1ic1", "g1igc2", "g1un2", "g1igc3", "g1ge1", "g1po1", "g1un3", "g1igc4", "g2fu", "g2hu", "g2ass1", "g2fu1", "g2hu1", "g2po1", "g2ass2", "g2pf", "g2fu2", "g2hu2", "g2ge", "g2un3", "g2hu3", "g2po2", "g2fu3", "g2hu4", "g2po3", "g2ic2", "g2ge1", "g2pf2", "g2fu4", "g2pf3", "g3ic3", "g3ic4", "g3ic5", "g3ic6", "g3ass", "g3ass2", "g3ge", "g2po5", "g2po6", "g1un4")


#Study2 Globe names, these are replaced with the names above to replicate the coding style from Study1
s2_GlobeNames <- paste0("NO", 1:43)

#tibble(s2_GlobeNames, s1_GlobeNames) %>% View()

all_data2 <-  all_data2%>% 
  rename(!!!setNames(s2_GlobeNames, s1_GlobeNames)) 


#---Classify items for domains and compute scale scores for each domain

#This ensures that the items are correctly classified within their respective  domains
all_vars_d <- tibble(all_vars = names(all_data2)) %>%
    mutate(
    domain = case_when(
      str_starts(all_vars, "ISM") ~ "Isms",
      str_detect(all_vars, "^P\\d{1,2}") ~ "Personality6",
      str_starts(all_vars, "TL") ~ "Tight_Lose",
      str_starts(all_vars, "MT") ~ "Material",
      str_starts(all_vars, "AM") ~ "Amoralism",
      str_starts(all_vars, "IV") ~ "Fanaticism",
      str_detect(all_vars, "^VAL\\d{1,2}$") ~ "Values", #Schwartz
      str_detect(all_vars, "^M\\d{1,2}$") ~ "Machiavellianism",
      str_detect(all_vars, "^EN") ~ "Ethnonational",
      str_starts(all_vars, "IC") ~ "Indv_Collectivism",
      str_detect(all_vars, "^MF\\d{2}$") ~ "Moral_Foundations",
      str_starts(all_vars, "FV") ~ "Family_Values",
      str_detect(all_vars, "^PA\\d{1,2}$") ~ "Prone_Aggr",
      str_starts(all_vars, "g1|g2|g3") ~ "Globe", 
      str_detect(all_vars, "^NO(?:4[4-9])$") ~ "Globe_extra", 
      str_starts(all_vars, "Ax") ~ "Social_Axioms",
      #Duke Religiosity Index
      str_detect(all_vars, "^DRI\\d{2}$") ~ "DRI",
      TRUE ~ all_vars
    ))


#get all item numbers for each domain
item_names <- \(domain_name){
  all_item_names <- all_vars_d %>% 
  filter(domain == {{domain_name}}) %>% 
  pull(all_vars)
  return(all_item_names)
}


compute_trait_score <- function(data, pos_items, rev_items = NULL) {
  if (is.null(rev_items)) {
    # If no reverse items are specified, just sum the positive items
    return(rowSums(data %>% select(all_of(pos_items)), na.rm = TRUE))
  } else {
    # If both positive and reverse items are specified
    rowSums(
      data %>% 
        select(all_of(c(pos_items, rev_items))) %>%
      #here the items are assumed to be on the scale of 1 to 5;
      #this function is only applied after ensuring that all items are
      #are measured on or a rescaled to 1to5 
        mutate(across(all_of(rev_items), ~ 6 - .x)),
      na.rm = TRUE
    )
  }
}

```

```{r data2}
#| cache: true
# convert any input into a character string
convert_to_char <- \(...) {
  expr <- enquos(...)
  char_vector <- map_chr(expr, quo_name)
  return(char_vector)
}

#---Compute scale scores
data2 <- bind_cols(
  all_data2_factor_cols,
  all_data2 %>% 
    select(D_AGE, 
      list_c(map(c("Isms","Globe","Globe_extra", "Tight_Lose", "Material","Social_Axioms", "Amoralism", "Fanaticism", "Ethnonational", "Indv_Collectivism", "Prone_Aggr", "Values", "Family_Values","Personality6", "DRI", "Moral_Foundations", "Machiavellianism"), item_names)))
) %>% 
  rename("country" = "Nation33",
         "language_admin" = "Language",
         "sex" = "D_SX",
         "family_home" = "D_FH", 
         "mother_edu" = "D_ME", 
         "father_edu" = "D_FE", 
         "age" = "D_AGE") %>% 
  #Retain countries with n >100 
  group_by(country) %>%
  filter(n() >= 100) %>%
  ungroup() %>% 
   # Drop rows with more than 10% missing data
  #filter(rowSums(is.na(.)) / ncol(.) <= 0.1)
#Rescale
  mutate(across(c(
    all_of(item_names("Values")),
    all_of(item_names("Isms")),
    all_of(item_names("Fanaticism")),
    all_of(item_names("Machiavellianism")),
    all_of(item_names("Moral_Foundations")),
    all_of(item_names("Globe")),
    all_of(item_names("Globe_extra")),
    all_of(item_names("Prone_Aggr")),
    all_of(item_names("Tight_Lose"))),
    # rescale all items from 1 to 5 for easy comparison
      ~scales::rescale(., to = c(1, 5))))  %>% 

  #-----[CNI ~ Continuous moderators] -------#  
  # scP; scM = scaled Personality; Mindset scores
mutate(
#compute_trait_score(data, pos_items, rev_items)
    #Personality: pty6
scP_Consc.indv = compute_trait_score(.,
            paste0("P", c(1,13,25)), 
            paste0("P", c(7,19,31))),
scP_Hon.indv = compute_trait_score(.,
            paste0("P", c(11,17,29)), 
            paste0("P", c(5,23,35))),
scP_Agree.indv = compute_trait_score(.,
            paste0("P", c(8,32)), 
            paste0("P", c(2,14,20,26))),
scP_Res.indv = compute_trait_score(.,
            paste0("P", c(12,36)), 
            paste0("P", c(6,18,24,30))),
scP_Extra.indv = compute_trait_score(.,
            paste0("P", c(3,15,27)), 
            paste0("P", c(9,21,33))), 
scP_Vir.indv = compute_trait_score(.,
            paste0("P", c(10,16,22,34)),
            paste0("P", c(4,28))),

   #Personality: pty2
  #Social self-regulation
 scP_Big2_SocialSelfReg.indv = (compute_trait_score(.,
            paste0("P", c(5,8,9,25,30, 38)), 
            paste0("P", c(6,7,14,19,23))))/10,
 #Social Dynamism
 scP_Big2_Dynamism.indv = (compute_trait_score(.,
            paste0("P", c(10,15,34,36,37, 39, 24)), 
            paste0("P", c(9,28,30,40))))/10,

   #Moral Foundations
scM_MFQ_Harm.indv = compute_trait_score(.,
   c("MF01","MF07","MF12","MF18")),
scM_MFQ_Fairness.indv = compute_trait_score(.,
   c("MF02","MF08","MF13","MF19")),
scM_MFQ_Loyalty.indv = compute_trait_score(., 
   c("MF03","MF09","MF14","MF20")),
scM_MFQ_Authority.indv = compute_trait_score(.,
   c("MF04","MF10","MF15","MF21")),
scM_MFQ_Purity.indv = compute_trait_score(.,
   c("MF05","MF11","MF16","MF22")),

    
    #Mindset: Social Axioms
  # Social Cynicism
scM_SocAx_Cynicism.indv = compute_trait_score(.,
   c("Ax5", "Ax12", "Ax16", "Ax23")),
  # Reward for Application
scM_SocAx_RewardForApp.indv = compute_trait_score(.,
   c("Ax4", "Ax9", "Ax13", "Ax21", "Ax28")),
  # Social Complexity
scM_SocAx_Complexity.indv = compute_trait_score(.,
   c("Ax6", "Ax8", "Ax10", "Ax15", "Ax19", "Ax22", "Ax25",
"Ax27", "Ax30")), 
  # Fate Control
scM_SocAx_FateControl.indv = compute_trait_score(.,
   c("Ax1", "Ax7", "Ax11", "Ax14", "Ax24")), 
  # Religiosity (importance of religion)
scM_SocAx_Religiosity.indv = compute_trait_score(.,
   c("Ax2", "Ax3", "Ax17", "Ax18", "Ax20", "Ax26", "Ax29"
)), 

      #Mindset: Individualism Collectivism
scM_IndvColl_CollecHori.indv = compute_trait_score(.,
   c("IC14", "IC16", "IC4", "IC6")), 
scM_IndvColl_CollecVert.indv = compute_trait_score(.,
   c("IC10", "IC13", "IC2", "IC7")), 
scM_IndvColl_IndivHori.indv = compute_trait_score(.,
   c("IC1", "IC11", "IC5", "IC8")),
scM_IndvColl_IndivVert.indv = compute_trait_score(.,
   c("IC12", "IC15", "IC3", "IC9")),

      #Mindset: Family Values
scM_FamValCohesion.indv = compute_trait_score(., c("FV02","FV04", "FV06", "FV08")),
scM_FamValHierarchy.indv = compute_trait_score(., c("FV01","FV03", "FV05", "FV07" )),

      #Mindset: Schwartz Values
  #Self-Transcendence: Universalism + Benevolence
  scM_Value_SfTran.indv = compute_trait_score(.,c("VAL5", "VAL8")),

  #Conservation: Conformity + Tradition + Security
scM_Value_Consrv.indv = compute_trait_score(.,c("VAL4", "VAL1", "VAL7")),

  #Self-enhancement: Achievement + Power
scM_Value_SelfEnh.indv = compute_trait_score(.,c("VAL3", "VAL10")),

  #Openness to Change: Stimulation + Self-direction
scM_Value_OpnChg.indv = compute_trait_score(.,c("VAL9", "VAL2")),

   #Fanaticism
        scM_fntc.indv = compute_trait_score(.,
     item_names("Fanaticism")[-c(4,6,17)],
     item_names("Fanaticism")[c(4,6,17)]),

#dput(convert_to_char())

       #Mindset: Isms
  #Traditional Religiousness
scM_Isms_TradRelig.indv = compute_trait_score(.,c("ISM12", "ISM17", "ISM22", "ISM35"), c("ISM14", "ISM16", "ISM30", "ISM8")),
  # Unmitigated Self-Interest
scM_Isms_UnmiSelfInt.indv = compute_trait_score(.,c("ISM11", "ISM3", "ISM32", "ISM4", "ISM41", "ISM42", "ISM46"), c("ISM21", "ISM26", "ISM7")),
  # Communal Rationalism
scM_Isms_CommRation.indv = compute_trait_score(.,c("ISM13", "ISM15", "ISM18", "ISM24", "ISM38", "ISM44"), c("ISM20", "ISM43")),
  # Subjective Spirituality
scM_Isms_SubjSpirit.indv = compute_trait_score(.,c("ISM10", "ISM39", "ISM5", "ISM6"), c("ISM2", "ISM23", "ISM25", "ISM27")),
  # Inequality Aversion
scM_Isms_IneqAver.indv = compute_trait_score(.,c("ISM19",  "ISM31", "ISM33", "ISM34", "ISM45"), c("ISM29", "ISM40")),

  #Mindset: Materialism
scM_Material.indv = compute_trait_score(.,
item_names("Material")),

  #Mindset: Machiavellianism
scM_Machiaveln.indv = compute_trait_score(., paste0("M", c(1,2,4)), paste0("M", c(3,5))),

   #Mindset: Proneness to Aggression - Honor
scM_Prone_Aggr.indv = compute_trait_score(.,item_names("Prone_Aggr")),

   #Mindset: Ethnonationalism
scM_Ethnonational.indv = compute_trait_score(., paste0("EN", c(1,3,4,6)), paste0("EN", c(2,5))),

  #Mindset: Cultural Tightness
scM_Tightness.indv = compute_trait_score(., paste0("TL0", c(1,2,3,5,6)), "TL04"),

  #Mindset: Amorialism
scM_Amoralism.indv = compute_trait_score(., item_names("Amoralism")[-c(1,4,6,8,10,11,13)],
 item_names("Amoralism")[c(1,4,6,8,10,11,13)]),

    #Mindset: Duke Religion Index (DRI)
    # Organizational activity
scM_DRI_OrgRelgAc.indv =  compute_trait_score(., "DRI01"),
    # Non-organizational activity 
scM_DRI_NonOrgRelgAc.indv = compute_trait_score(., "DRI02"),
    # Intrinsic religiosity
scM_DRI_IntrnscRelg.indv = compute_trait_score(.,  paste0("DRI0", c(3,4,5))),
    # Civic Multicultural Nationalism
scM_CivicMCNational.indv = compute_trait_score(., "EN2", "EN5"),

      #Mindset: GLOBE
    #InGroup Collectivism
scM_globe_igc.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*igc.*$")),
   # Institutional Collectivism
scM_globe_ic.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*ic.*$")[-c(3,4)],
            str_subset(item_names("Globe"), "^g.*ic.*$")[c(3,4)]),
    # Performance Orientation/Achievement
scM_globe_pf.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*pf.*$")[-4], 
            str_subset(item_names("Globe"), "^g.*pf.*$")[4]),
    # Uncertainty Avoidance
scM_globe_un.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*un.*$")[-5], 
            str_subset(item_names("Globe"), "^g.*un.*$")[5]),
    # Gender Egalitarian
scM_globe_ge.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*ge.*$")[-c(1,2,4)], 
            str_subset(item_names("Globe"), "^g.*ge.*$")[c(1,2,4)]),
    # Power Distance
scM_globe_po.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*po.*$")[-c(5,6)], 
            str_subset(item_names("Globe"), "^g.*po.*$")[c(5,6)]),
    # Future Orientation
scM_globe_fu.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*fu.*$")[-c(3,4)], 
            str_subset(item_names("Globe"), "^g.*fu.*$")[c(3,4)]),
    # Assertiveness
scM_globe_ass.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*ass.*$")[-c(2,3)], 
            str_subset(item_names("Globe"), "^g.*ass.*$")[c(2,3)]),
    # Humane Orientation
scM_globe_hu.indv = compute_trait_score(.,
            str_subset(item_names("Globe"), "^g.*hu.*$"))
) %>% 
  mutate(pID = paste0("p", 1:nrow(.)), .before = everything())%>% 
  
  #compute community[here, country] scale scores
  with_groups(country, 
    mutate,
    across(
      # Select all pty and cog scaled scores  
      contains(c( "scP", "scM")),
      # Compute mean by country
      ~mean(., na.rm = TRUE),
      # Create new name [scP_Hon.indv -> scP_Hon.comm]
      .names = "{str_remove(.col, '[.].*')}.comm"
    )
  ) %>% 
  
    #-----[CNI ~ Categorical moderators]------# 

#Demographic variables
mutate(
  mother_edu = case_when(
    str_detect(mother_edu, "don't know") ~ NA_character_,
    TRUE ~ as.character(mother_edu)
  ),
  father_edu = case_when(
    str_detect(father_edu, "don't know") ~ NA_character_,
    TRUE ~ as.character(father_edu)
  ),
  age_group = case_when(
    age >= 13 & age <= 17 ~ "13-17",
    age >= 18 & age <= 25 ~ "18-25",
    age >= 26 & age <= 35 ~ "26-35",
    age >= 36 & age <= 45 ~ "36-45",
    age >= 46 ~ "46+",
    TRUE ~ NA_character_
  ))%>%
  relocate(age_group, .before = age)
```

```{r tbl-SampleStatistics, echo=F, results='asis'}
#| tbl-cap: "Sample statistics by Country"
#| label: tbl-SampleStatistics

data2 %>% 
  group_by(country) %>% #names()
select(age, sex) %>% 
  summarize(mean_age = mean(age, na.rm=TRUE),
            percent.male = mean(sex == "male", na.rm=TRUE)*100,
            N = n()) %>% 
  arrange(desc(N)) %>% 
  kable(format = "latex", 
        col.names = c("Country", "Mean Age", "% Male", "n"), 
        booktabs = TRUE) %>% 
  kable_styling()
```

```{r tbl-SampleDemographics, echo = F, results='asis'}
#| label: tbl-SampleDemographics
#| tbl-cap: "Sample Demographics"

data2 %>%
  select(sex, age_group, family_home, mother_edu, father_edu, language_admin)  %>%
  mutate(across(everything(), ~as.factor(.))) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "category") %>%
  group_by(variable, category) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(variable) %>%
  mutate(
    p = 100 * n / sum(n),
    sample = paste0(n, " (", papaja::printnum(p), "\\%)")) %>%
  ungroup() %>%
  select(-n, -p) %>%
  #arrange(variable, category) %>%
  mutate(
   category = if_else(is.na(category), "missing",
       as.character(category)),
   variable = factor(variable, levels = c("sex", "age_group", "family_home", "mother_edu", "father_edu", "language_admin"))
  ) %>%
  arrange(variable) %>%
  dplyr::select(-variable) %>%
kable(longtable = T,
format = "latex",
align = c("l", "c", "c"), escape = FALSE,
col.names = c("Variable", "$\\textit{n}$ (\\%)"),
booktabs = TRUE) %>%
kable_styling(latex_options = c("repeat_header", "longtable")) %>%
group_rows("Sex", 1, 3) %>%
group_rows("Age", 4, 8) %>%
group_rows("Family Home", 9, 13) %>%
group_rows("Mother's Education", 14, 23) %>%
group_rows("Father's Education", 24, 33) %>%
group_rows("Language of Administration", 34, 51)

```

```{r}
#| include: false
#knitr::opts_chunk$set(eval = FALSE, echo = FALSE)
```

# Analysis

## RQ 1: How to quantify CNI?

Similar to Study 1, CNI is estimated using a Random slope Multilevel model (varying slopes and fixed intercepts) wherein items nested within person \[pID\] (Weston,2024). This model accounts for the nested nature of our data, where individual items are clustered within each participant. As responses are ipsatized (standardized within participant), the resulting slope estimates can be interpreted as correlation estimates.

For study 2, eight CNI models are computed:

::: {#note-CNI-models .callout-note title="CNI Models" icon="false"}
1.  Mindset CNI: consisting of all mindset items
2.  Isms CNI
3.  Globe CNI: Original Globe items by House et al.
4.  GlobeEx CNI: House et al. + extra items
5.  Moral Foundations CNI
6.  Fanaticism CNI
7.  Social Axioms CNI
8.  Personality 6 CNI: consisting of Big 6 items
:::

The Mindset-CNI and Personality6-CNI encompass distinct domains of psychological measurement, while the remaining CNI types can be viewed as subcomponents or specialized facets within the broader Mindset-CNI framework. Mindset-CNI therefore is the most comprehensive of all the CNI types explored here.

```{r funs.-model_CNI}
# functions for computing CNIs

#item names for every CNI type
get_item_names <- \(CNI_type, data) {
  domains <- switch(CNI_type,
    "Mindset" = c("Isms", "Fanaticism", "Social_Axioms", "Values", "Tight_Lose", "Material", 
                  "Amoralism", "Ethnonational", "Indv_Collectivism", "Globe", "Globe_extra", 
                  "Moral_Foundations", "Family_Values","Machiavellianism","Prone_Aggr"),
    "pty6" = c("Personality6"),
    "Fanaticism" =c("Fanaticism"),
    "Isms" =c("Isms"),
    "Globe" =c("Globe"),
    "Globe_extra" =c("Globe", "Globe_extra"),
    "Moral_foundations" =c("Moral_Foundations"),
    "Social_Axioms" = c("Social_Axioms"),

    stop("CNI type not found")
  )
  
  item_names <- data %>% 
    filter(domain %in% domains) %>% 
    pull(all_vars)
  
  if (length(item_names) == 0) {
    warning("No items found for the specified domains")
  }
  
  return(item_names)
} 

#ipsatize/within person standardize scores
  #scores are ipsatized before CNI's are computed
ipsatize <- \(x){
  value <- (x-mean(x, na.rm=T))/(sd(x, na.rm=T)) 
  return(value)
} 

#compute z_profiles for pID
compute_profiles <- \(var_names){
#compute mean country profiles
country_profiles <- data2 %>% 
  group_by(country) %>%
  summarise(
    across(all_of(var_names), ~mean(.x, na.rm = TRUE), .names = "avg_{.col}"),#variables for cogCNI
   n_p = n())%>% # number of participants) 
  ungroup() %>% 
  #retain participants who have responded to at least 30 items.- all countries have n_p>30
  filter(n_p>=30) %>% 
   pivot_longer(
    cols = starts_with("avg_"),
    #item names stored in item
    names_to = "item",
    values_to = "ctry_response"
  ) %>% 
   mutate(item = str_remove(item, "avg_")) %>% 
ungroup()

self.ctry_profiles <-  data2 %>%
  select(all_of(var_names), pID, country) %>%
  pivot_longer(names_to = "item",
               values_to = "response",
               cols = all_of(var_names)) %>% 
  filter(!is.na(response)) %>%
  left_join(country_profiles, by = c("country", "item")) %>%
   filter(!is.na(ctry_response)) %>%
# ipsatize responses within profile 
  with_groups(pID, mutate, across(
    # mutate self-rating and mean country profiles for each pID at once
  contains("response"),
  # with the ipsatize function ,
  ipsatize,
  # create new name
.names = "z_{.col}")) 

overallM_profiles <- self.ctry_profiles %>% 
  select(item, z_response) %>%
  filter(!is.na(z_response)) %>%
  group_by(item) %>%
  summarise(overall.M = mean(z_response)) %>% 
  ungroup() 


return(lst(self.ctry_profiles, overallM_profiles)) #set_names() to the input object names

} 
```

```{r CNI-profiles}
#| cache: true
#get all item names for CNI types
mindsetCNI_items <- get_item_names("Mindset", all_vars_d)
pty6CNI_items <- get_item_names("pty6", all_vars_d)
ismCNI_items <- get_item_names("Isms", all_vars_d)
fantcCNI_items <- get_item_names("Fanaticism", all_vars_d)
globeCNI_items <- get_item_names("Globe", all_vars_d)
globeExCNI_items <- get_item_names("Globe_extra", all_vars_d)
mfCNI_items <- get_item_names("Moral_foundations", all_vars_d)
socAxCNI_items <- get_item_names("Social_Axioms", all_vars_d)

#compute pofiles for each CNI type
mindsetCNI_profiles <- compute_profiles(mindsetCNI_items)
pty6CNI_profiles <- compute_profiles(pty6CNI_items)
ismCNI_profiles <- compute_profiles(ismCNI_items)
fantcCNI_profiles <- compute_profiles(fantcCNI_items)
globeCNI_profiles <- compute_profiles(globeCNI_items)
globeExCNI_profiles <- compute_profiles(globeExCNI_items)
mfCNI_profiles <- compute_profiles(mfCNI_items)
socAxCNI_profiles <- compute_profiles(socAxCNI_items)

all_profiles <- lst(
  mindsetCNI_profiles,
  pty6CNI_profiles,
  ismCNI_profiles,
  fantcCNI_profiles,
  globeCNI_profiles,
  globeExCNI_profiles,
  mfCNI_profiles,
  socAxCNI_profiles 
)
```

```{r DONT-RUN-fit-all-cni-mods, eval=FALSE, echo=TRUE}
#formula for computing CNI
add_CNIformula <- \(data){
  lmer(z_response ~ z_ctry_response + overall.M + (-1 + z_ctry_response|country/pID), data = data)
}

mindsetCNI_mod <- mindsetCNI_profiles$self.ctry_profiles %>% 
  full_join(cogCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)
  
pty6CNI_mod <- pty6CNI_profiles$self.ctry_profiles %>% 
  full_join(pty6CNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

ismCNI_mod <- ismCNI_profiles$self.ctry_profiles %>% 
  full_join(ismCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

fantcCNI_mod <- fantcCNI_profiles$self.ctry_profiles %>% 
  full_join(fantcCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

globeCNI_mod <- globeCNI_profiles$self.ctry_profiles %>% 
  full_join(globeCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

globeExCNI_mod <- globeExCNI_profiles$self.ctry_profiles %>% 
  full_join(globeExCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

mfCNI_mod <- mfCNI_profiles$self.ctry_profiles %>% 
  full_join(mfCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)

socAxCNI_mod <- socAxCNI_profiles$self.ctry_profiles %>% 
  full_join(socAxCNI_profiles$overallM_profiles, by = "item") %>% add_CNIformula(.)
```

```{r save-CNImods, echo = F, eval = F}
save(mindsetCNI_mod, pty6CNI_mod, ismCNI_mod, fantcCNI_mod, globeCNI_mod, globeExCNI_mod, mfCNI_mod, socAxCNI_mod, 
     file = here("objects/Study2/all_CNI.mods_study2.Rdata"))
```

```{r load-CNImods, echo = F}
load(here::here("objects/Study2/all_CNI.mods_study2.Rdata"))
```

### Model Complexity

The Eight models vary in the number of items and domains of psychological measures. 1. The Parallel Analysis computed here, identify the optimum number of dimensions that the data for every CNI type can be reduced to. The optimum number of dimensions are retained based on the comparison of eigenvalues of the actual data and those of randomly generated data sets. Dimensions are retained when their eigenvalues exceed those of the random data, ensuring that only factors accounting for more variance than would be expected by chance are retained. 2. Principal Components that explain at least 50% of variance are identified.

```{r fun.-heterogeneity}
# Function to calculate heterogeneity
compute_heterogeneity <- function(data) {
  # Compute correlation matrix once - memory efficient
  cor_matrix <- cor(data, use = "pairwise.complete.obs")
  
  pca_rotation <- function(rotation) {
    # Perform PCA using correlation matrix
    pca <- principal(cor_matrix, nfactors = ncol(data), rotate = rotation, covar = FALSE)
    
    # Calculate cumulative variance explained
    cumulative_var <- cumsum(pca$values) / sum(pca$values)
    
    # Find number of factors needed to explain at least 50% variance
    heterogeneity <- which(cumulative_var >= 0.5)[1]
    
    return(heterogeneity)
  }
  
  # Perform parallel analysis using correlation matrix
  pa_result <- fa.parallel(cor_matrix, n.obs = nrow(data), fa = "fa",
      fm = "minres", show.legend = FALSE, plot = FALSE)
  
  tibble(
    n_items = ncol(data),
    pa = pa_result$nfact,
    pca_50 = pca_rotation("none")
  )
}

```

```{r DONT-RUN-compute-heterogeneity, eval = F}

heterogeneity_stats <- map_dfr(
  list(
   Mindset = select(data2, 
               get_item_names("Mindset",
                              all_vars_d)),
   Globe = select(data2,
                get_item_names("Globe",
                              all_vars_d)),
   GlobeEx = select(data2,
                get_item_names(c("Globe_extra"),
                              all_vars_d)),
   Isms = select(data2,
                get_item_names("Isms",
                              all_vars_d)),
   Fanaticism = select(data2,
                get_item_names("Fanaticism",
                              all_vars_d)),
   Moral_foundations = select(data2,
                get_item_names("Moral_foundations",
                              all_vars_d)),
     Social_Axioms = select(data2,
                get_item_names("Social_Axioms",
                              all_vars_d)),
   Personality6 = select(data2,
                get_item_names("pty6",
                              all_vars_d))
),
 compute_heterogeneity, .id = "cni_type"
)
```

```{r save-compute-heterogeneity, echo = F, eval = F}
save(heterogeneity_stats, 
     file = here("objects/Study2/heterogeneity_stats_study2.Rdata"))
```

```{r load-compute-heterogeneity, echo = F}
load(here("objects/Study2/heterogeneity_stats_study2.Rdata"))
```

```{r tbl-heterogeneity, results='asis', echo=F}
#| label: tbl-heterogeneity
#| tbl-cap: "CNI Model complexity"

heterogeneity_stats %>% 
   mutate(cni_type = str_replace_all(cni_type, "_", " ")) %>% 
  kable(booktabs = T, 
        escape = F,
        format = "latex",
        col.names = c("CNI type", "No. items", "Parallel analysis", "PCA")) %>% 
  kable_styling() %>% 
     group_rows("Mindset", 1, 7) %>%
     group_rows("Personality", 8, 8) 

```

```{r plot-heterogeneity, echo=F}
#| fig-height: 6
#| fig-width: 10
#| out-width: "100%"
#| cap-location: bottom
#| fig-cap: "Model Complexity Measures Across CNI Types"
#| label: plot-heterogeneity

heterogeneity_stats %>%
  pivot_longer(cols = c(pa, pca_50), names_to = "metric", values_to = "value") %>%
  mutate(x_label = paste0(cni_type, "\n(", n_items, " items)"),
         x_label = reorder(x_label, n_items))  %>% 
# Create the plot
ggplot(., aes(x = x_label, y = value, color = metric, group = metric)) +
  geom_line() +
  geom_point(size = 3) + 
  scale_color_manual(values = c("pa" = "#e78f8e", "pca_50" = "#93bfa6"),
                     labels = c("pa" = "Parallel Analysis", "pca_50" = "PCA 50%"),
                     name = "Metric") +
  labs(x = "CNI Type",
       y = "Number of Factors") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        text = element_text(family = "serif", size = 14))

```

@fig-plot-heterogeneity indicates that as the item count increases, so does the number of identifiable dimensions, indicating higher model complexity. The Fanaticism CNI, despite having only 17 items, has been included here to maintain consistency with Study 1 and provide a basis for comparison. Notably, the Mindset CNI exhibits a markedly higher complexity, with nearly four times as many dimensions as the other CNI models.

### CNI plots

```{r fun.-plot_CNI, echo=FALSE}
#Functions
#model1_est = tidy(model1, conf.int = T)

plot_CNI <- function(model_obj) {
  # Get the name of the object passed to the function
  obj_name <- deparse(substitute(model_obj))
  
  # Extract the title (everything before the underscore)
  title <- str_extract(obj_name, "^[^_]+")
  
  # Define color mapping
  color_map <- tibble(
    mod_name = c("mindsetCNI", "ismCNI", "fantcCNI", "globeCNI", "globeExCNI", "mfCNI", "socAxCNI","pty6CNI"),
    color = c("#0074B7","#6082B6", "#70d6ff", "#a0c4ff","#189AB4", "#6495ED", "#5D3FD3", "#ff70a6")
  )
  
  # Determine the color based on the title
  plot_color <- color_map %>% 
    filter(str_detect(mod_name, title)) %>% 
    pull(color)
  
  # Calculate slopes
  mod_slopes <- slopes(model_obj, variables = "z_ctry_response", by = "pID")
  
  coefficient_plot <- mod_slopes %>%
      ggplot(aes(x = reorder(pID, estimate), y = estimate)) +
      geom_segment(aes(xend = pID,
y = conf.low,yend = conf.high),
                   alpha = .08 , color = plot_color) +
      geom_point(size = .22, color = plot_color) +
      scale_x_discrete(breaks = NULL) +
      #coord_cartesian(ylim = c(-0.2, .92)) +
      labs(x = "Participant", y = "CNI coefficient", title = title) +
      theme_bw()
  
   hist_plot <- mod_slopes %>%
    as.data.frame() %>%
    ggplot(aes(x = estimate)) +
    geom_histogram(binwidth = .03, color = "white", fill = plot_color) +
    labs(x = "CNI coefficient", y = "Frequency", title = title) +
    scale_x_continuous(limits = c(-0.3, 0.92))+
     scale_y_continuous(limits = c(0, 1000))+
    theme_bw()
  
  return(lst(coefficient_plot,hist_plot ))
}
```

```{r  DONT-RUN-CNIplots, echo = T, eval = FALSE}
#mindsetCNI_mod, pty6CNI_mod, ismCNI_mod, fantcCNI_mod, globeCNI_mod, globeExCNI_mod, mfCNI_mod, socAxCNI_mod

mindsetCNI_plot <- plot_CNI(mindsetCNI_mod) 
ismCNI_plot <- plot_CNI(ismCNI_mod) 
globeCNI_plot <- plot_CNI(globeCNI_mod)
globeExCNI_plot <- plot_CNI(globeExCNI_mod)
fantcCNI_plot <- plot_CNI(fantcCNI_mod)
mfCNI_plot <- plot_CNI(mfCNI_mod)
socAxCNI_plot <- plot_CNI(socAxCNI_mod)
pty6CNI_plot <- plot_CNI(pty6CNI_mod)
```

```{r save-CNImods_plots, echo = F, eval = F}
save(mindsetCNI_plot, ismCNI_plot, globeCNI_plot, globeExCNI_plot, fantcCNI_plot, mfCNI_plot, socAxCNI_plot, pty6CNI_plot,  
     file = here("objects/Study2/all_CNImods_plots_Study2.Rdata"))
```

```{r load-CNImods_plots, echo = F}
#takes time to load
load(here("objects/Study2/all_CNImods_plots_Study2.Rdata"))
```

```{r fun.-patch_CNIplots}
patch_CNIplots <- \(plot_list){
  
  p1 <- plot_list$coefficient_plot & 
  theme(plot.title = element_blank(), 
        text = element_text(family = "serif", size = 12))
  
  p2 <- plot_list$hist_plot & 
  theme(plot.title = element_blank(), 
        text = element_text(family = "serif", size = 12))
  
  combined_plot <- p1 + p2 
  
  return(combined_plot)
}
```

```{r print-patch_CNIplots-details}
#| cache: true
# Create a list of plot objects and their corresponding titles
CNIplot_data <- lst(
  list(plot = mindsetCNI_plot, title = "Mindset CNI"),
  list(plot = ismCNI_plot, title = "Isms-Mindset CNI"),
  list(plot = globeCNI_plot, title = "Globe-Mindset CNI"),
  list(plot = globeExCNI_plot, title = "Globe (Extra items)-Mindset CNI"),
  list(plot = fantcCNI_plot, title = "Fanaticism-Mindset CNI"),
  list(plot = mfCNI_plot, title = "Moral Foundations-Mindset CNI"),
  list(plot = socAxCNI_plot, title = "Social Axioms-Mindset CNI"),
  list(plot = pty6CNI_plot, title = "Personality6 CNI")
)

CNIplot_data <- lst(
   mindsetCNI_plot, ismCNI_plot, globeCNI_plot, globeExCNI_plot,
   fantcCNI_plot, mfCNI_plot, socAxCNI_plot, pty6CNI_plot)

CNIplot_data_details <- tibble(
  mod_names = names(CNIplot_data),
  caption = c("Mindset CNI", "Isms-Mindset CNI", "Globe-Mindset CNI", 
              "Globe (Extra items)-Mindset CNI", "Fanaticism-Mindset CNI", 
              "Moral Foundations-Mindset CNI", "Social Axioms-Mindset CNI", 
              "Personality6 CNI")
)
```

```{r print-patch_CNIplots}
#| cache: true
#| fig-height: 5
#| fig-width: 10
#| out-width: "100%"
#| fig-cap-location: bottom
#| fig-cap: 
#|   !expr CNIplot_data_details %>%
#|     pull(caption)


# `walk` to apply patch_CNIplots to each plot in the list and print quietly
walk(names(CNIplot_data), \(mod_names) {
    cat("\n\n")
    print(
      pluck(CNIplot_data, mod_names) %>% 
        patch_CNIplots())
    cat("\n\n")
  })

```

## Person level slopes

```{r DONT-RUN-person-slopes, eval=FALSE, echo=TRUE}
#computing person level range

all_cni_models <- lst(mindsetCNI_mod, pty6CNI_mod, ismCNI_mod, fantcCNI_mod, globeCNI_mod, globeExCNI_mod, mfCNI_mod, socAxCNI_mod)

compute_slopes <- function(model_obj) {
  obj_name <- deparse(substitute(model_obj))
  
  # Calculate slopes
  mod_slopes <- slopes(model_obj, variables = "z_ctry_response", by = "pID")

  return(mod_slopes)
}

all_slopes <- map_dfr(all_cni_models, compute_slopes, .id = "model_name")


```

```{r save-person-slopes, echo = F, eval = F}
save(all_slopes,  
     file = here("objects/Study2/person-slopes-cni.Rdata"))
```

```{r load-person-slopes, echo = F}
#takes time to load
load(here("objects/Study2/person-slopes-cni.Rdata"))
```

```{r range-CNI, eval=F, echo=F}
tibble(all_slopes) %>% 
  group_by(model_name) %>% 
   summarize(
        low = min(estimate),
        high = max(estimate),
        range = high - low) %>%
  ungroup() %>% 
  rename(model = model_name) %>% 
  arrange(desc(range)) %>% 
 mutate(model = case_when(
    model == "mindsetCNI_mod" ~ "Mindset CNI",
    model == "ismCNI_mod" ~ "Isms CNI",
    model == "globeCNI_mod" ~ "Globe CNI",
    model == "globeExCNI_mod" ~ "Globe Extra CNI",
    model == "mfCNI_mod" ~ "Moral Foundations CNI",
    model == "fantcCNI_mod" ~ "Fanaticism CNI",
    model == "pty6CNI_mod" ~ "Personality 6 CNI",
    model == "socAxCNI_mod" ~ "Social Axioms CNI",
    TRUE ~ model))
```

## CNI Models' Summary

```{r DONT-RUN-create-tbl-cni-mods, echo = T, eval = F}
CNImods_table2 <- modelsummary(
  list("Mindset" = mindsetCNI_mod,
       "Ism" = ismCNI_mod,
       "Globe" = globeCNI_mod,
       "Globe (Extra)" = globeExCNI_mod,
       "Fanaticism" = fantcCNI_mod,
       "Moral Foundations" = mfCNI_mod,
       "Social Axioms" = socAxCNI_mod,
       "Big 6" = pty6CNI_mod), 
             estimate = "{estimate}{stars}",
             statistic = "[{conf.low}, {conf.high}]",
            # group = group + term ~ model, 
             coef_omit = "Intercept|^status",
             coef_rename = c(
              "z_ctry_response" = "CNI",
               "overall.M" = "Overall Mean Profile",
               "SD (z_ctry_response pIDcountry)" = "SD of CNI (across people)",
               "SD (z_ctry_response country)" = "SD of CNI (across country)",
               "SD (Observations)" = ""),
             gof_map = c("nobs"), 
             fmt = "%.2f",
             title = "Cultural Normativity Index",
             output = "kableExtra") %>% 
  add_header_above(c(" ", "Mindset" = 7, "Personality" = 1))
```

```{r save-CNItable, echo = F, eval = F}
save(CNImods_table2,
     file = here("objects/Study2/CNImods_table2.Rdata"))
```

```{r load-CNItable, echo = F}
load(here("objects/Study2/CNImods_table2.Rdata"))
```

```{r tbl-cni-mods, results='asis', echo=F, eval=T}
#|tbl-cap: "Mindset and Personality Cultural Normativity Index (CNI) Models"

CNImods_table2
```

## Country trends

```{r DONT-RUN-cni.ctry-trends, eval=F, echo=T}
#CNI country estimates from `slopes` (also can get CI's here) and `coef` (no CI's) are very close, both provide total effects (fixed+random)
#cogCNI_mod_ctry.slopes <- slopes(cogCNI_mod , variables = "z_ctry_response", by = "country")

all_mods_ctry.trends <- map_dfr(lst(
  mindsetCNI_mod, ismCNI_mod, fantcCNI_mod, globeCNI_mod, globeExCNI_mod, mfCNI_mod, socAxCNI_mod, pty6CNI_mod), 
                 ~slopes(., variables = "z_ctry_response", by = "country"), .id = "model") 
```

```{r save-country-trends, echo = F, eval = F}
save(all_mods_ctry.trends,
     file = here("objects/Study2/CNI-ctry-trends2.Rdata"))
```

```{r load-country-trends, echo = F}
load(here("objects/Study2/CNI-ctry-trends2.Rdata"))
```

```{r tbl-ctry.trends-allCNImods, results='asis', echo=F, eval=T}
#| tbl-cap: "Country estimates across CNI types"

group_names <- c("Mindset CNI", "Isms-Mindset CNI", "Fanaticism-Mindset CNI", "Globe-Mindset CNI", "Globe Extra-Mindset CNI", "Moral Foundations-Mindset CNI", "Social Axioms-Mindset CNI", "Personality6 CNI")

all_mods_ctry.trends %>% 
  tibble() %>% 
  select(model, country, estimate, conf.low, conf.high, p.value) %>%
    mutate(
    p.value = map_chr(p.value, papaja::printp),
    across(where(is.numeric), ~ round(., 3)),
  ci = paste0("[", conf.low, ", ", conf.high,"]"),
    estimate = as.character(estimate)) %>% 
  select(country, estimate, ci, p.value) %>% 
   kable(booktabs = T, 
        escape = F,
        format = "latex",
        longtable = TRUE,
        col.names = c("Country", "Estimate", "95\\% CI", "$\\textit{p}$")) %>% 
  kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
   {reduce(seq_along(group_names), 
           .init = ., 
           ~ group_rows(.x, group_names[.y], 27*(.y-1)+1, 27*.y))} %>% 
  column_spec(1, width = "5cm")
```

```{r fun.-oneCoef-plot, echo = F, eval = F}
#One coefficient plot at a time!
plotCNI_ctry_trends <- \(slope_data){
  
  obj_name <- deparse(substitute(slope_data))
  title <- str_extract(obj_name, "^[^_]+")
  
  plot <- slope_data %>% 
  as_tibble() %>% 
  select(country, estimate, conf.low, conf.high) %>% 
   ggplot(aes(x = reorder(country,estimate), y = estimate)) +
   geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                color = "grey") +
   geom_point() + 
   scale_y_continuous(limits = c(0, 1)) +
   labs(x = NULL, 
        y = "CNI",
        title = paste0(title, " estimates across countries")) +
   coord_flip() +
   theme_bw() +
   theme(plot.title.position = "plot", 
         text = element_text(family = "serif", size = 12))
  
  return(plot)
}
#plotCNI_ctry_trends(mindsetCNI_mod_ctry.slopes)
```

```{r ctry-trends-2models-plot, echo=F, eval=F}
#| cache: true
#| fig-height: 12
#| fig-width: 10
#| out-width: "100%"
#| fig-cap-location: bottom
#| fig-cap: "CNI estimates across countries: Two CNIs"

all_mods_ctry.trends %>% 
  as_tibble() %>% 
  mutate(model = str_extract(model, "^[^_]+")) %>% 
  filter(model %in% c("mindsetCNI", "pty6CNI")) %>% 
  select(model, country, estimate, conf.low, conf.high) %>% 
  ggplot(aes(x = reorder(country, estimate), y = estimate, 
             color = model)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                position = position_dodge(width = 0.5), 
                width = 0.3) +
  geom_point(position = position_dodge(width = 0.5), 
             size = 1.7)+ 
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_manual(values = c("mindsetCNI" = "#0074B7", 
  "pty6CNI" = "#ff70a6")) + 
  labs(x = NULL, 
       y = "CNI",
       color = "Model") +
  coord_flip() +
  theme_bw() +
  theme(plot.title.position = "plot",
        legend.position = "bottom", 
        text = element_text(family = "serif", size = 12))
```

```{r ctry-trends-8models-plot, echo=F}
#| fig-height: 12
#| fig-width: 10
#| out-width: "100%"
#| fig-cap-location: bottom
#| fig-cap: "CNI estimates across countries: Eight CNIs"

all_mods_ctry.trends %>% 
  as_tibble() %>% 
  mutate(model = str_extract(model, "^[^_]+")) %>% 
  select(model, country, estimate, conf.low, conf.high) %>%
  mutate(alpha = ifelse(model %in% c("pty6CNI", "mindsetCNI"), 1, 0.5),
         errorbar_size = ifelse(model %in% c("pty6CNI", "mindsetCNI"), .8, 0.4)) %>%
  ggplot(aes(x = reorder(country, estimate), y = estimate, color = model, linetype = model)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, alpha = alpha, size = errorbar_size), position = position_dodge(width = 0.5),  width = 2.8) +
  geom_point(aes(alpha = alpha), 
             position = position_dodge(width = 0.5), 
             size = 1.7) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_manual(values = c("mindsetCNI" = "#0070BB", "ismCNI"  = "#1ca9c9", "fantcCNI"  = "#0000CD", "globeCNI"  = "#A3C1AD", "globeExCNI"  = "#008080", "mfCNI"  = "#082567", "socAxCNI"  = "#800080", "pty6CNI" = "#DE3163")) +
  scale_alpha_identity() +
  scale_size_identity() +
  scale_linetype_manual(values = c("globeCNI"  ="dashed", "globeExCNI"  ="dashed","ismCNI"  ="dashed", "fantcCNI"  ="dashed",
"mfCNI"  = "dashed", "socAxCNI"  = "dashed",
     "mindsetCNI" = "solid", "pty6CNI" = "solid")) +
  labs(x = NULL, y = "CNI",
       color = "Model") +
  coord_flip() +
  theme_bw() +
  theme(plot.title.position = "plot",
        legend.position = "bottom", 
        text = element_text(family = "serif", size = 12)) +
  guides(linetype = "none", alpha = "none", size = "none")
```

# RQ 2: Associations between CNI and personality and mindset variables

```{r fun.-cni-ContMod-effects}
# Moderators here have to continuous, this won't work for categorical moderators
#Explanation for function below
      #[which CNI-type]:
  #cni_profiles_data <- mindsetCNI_profiles1$self.ctry_profiles 
      #[which moderator]:
  #modtr_pattern <- "^scP.*indv$" (scP = pty; scM = mindset)
      #[causal relationship]:
  #CNI <- Continuous moderator

#This version of the function is specifically necessary for parallel processing! Here the modtr_patterns can be varied. The cognitive profiles are long and there are multiple moderators that need to be saved. This method works the best for this. 

cni.ContMod_effects <- function(cni_profiles_data, modtr_pattern) {
  
  # Determine the level based on the modtr_pattern
  level <- if(grepl("indv", modtr_pattern)) "Individual" else if(grepl("comm", modtr_pattern)) "Country" else "Unknown"

  #right data format
  cni.modtr_data <- data2 %>% 
    #select moderator scales individual level (pID) scores 
    #---$select moderators$ - specify regex
    select(pID, matches(modtr_pattern)) %>% 
    #mean centering the moderator score cols
    #since this standardization is col-wise, running pty7 is not an issue
    mutate_if(is.numeric, 
              ~. - mean(., na.rm = TRUE)) %>% 
    pivot_longer(-pID, 
                 names_to = "modtr", #moderator name
                 values_to = "modtr_score") %>% # moderator score
    full_join(cni_profiles_data, by = c("pID"), relationship = "many-to-many")
  
  #CNI <- moderator
  cni.modtr_models <- cni.modtr_data %>%
    tidyr::nest(data = -modtr) %>%
    mutate(
      #cni ~ mod
      mod.linear = map(data, ~lmer(z_response ~ z_ctry_response * modtr_score + (-1 + z_ctry_response | pID), data = .)),
      #cni ~ mod + mod^2
      mod.quadratic = map(data, ~lmer(z_response ~ z_ctry_response * modtr_score + z_ctry_response * I(modtr_score^2) + (-1 + z_ctry_response | pID), data = .)),
      
      #save results
      tidy_mod.linear = map(mod.linear, tidy, conf.int = TRUE),
      tidy_mod.quadratic = map(mod.quadratic, tidy, conf.int = TRUE)
    )
  
  results_linear <- cni.modtr_models %>% 
    select(modtr, tidy_mod.linear) %>% 
    unnest(cols = c(tidy_mod.linear)) %>%
    filter(term == "z_ctry_response:modtr_score") %>% 
    select(modtr, term, estimate, conf.low, conf.high, p.value)
  
  results_quadratic <- cni.modtr_models %>% 
    select(modtr, tidy_mod.quadratic) %>% 
    unnest(cols = c(tidy_mod.quadratic)) %>%
    filter(term == "z_ctry_response:I(modtr_score^2)") %>%
    select(modtr, term, estimate, conf.low, conf.high, p.value)
  
  output <- bind_rows(
    !!level := results_linear,
    !!level := results_quadratic,
    .id = "level"
  )
  
  return(output)
}
```

```{r table_contMods, eval = F, echo=FALSE, results='asis'}
df <- data.frame(
  `Mindset` = c(
    "[45indv + 46comm]",
     paste0(c("Mindset", "Isms", "Globe", "Globe (Extra items)", "Fanaticism", "Moral Foundations", "Social Axioms", "Personality 6"), " CNI ", "x Mindset variables")),
  `Personality` = c(
    "[8indv + 8comm]",
    paste0(c("Mindset", "Isms", "Globe", "Globe (Extra items)", "Fanaticism", "Moral Foundations", "Social Axioms", "Personality 6"), " CNI ", "<- Personality variables"))
 
)

table_contMods <- kable(df,
  format = "latex", align = c("l", "l"),
   col.names = c("CNI ~ Mindset variables ", "CNI ~ Personality variables")) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(0, bold = TRUE,
           ) %>%
  row_spec(1) %>%
  add_header_above(c(" " = 2), bold = TRUE)
```

Given the large *n*, especially for mindsetCNI profiles and the total number of moderators, it will be necessary to use parallel processing for this analysis. It significantly reduces computation time for multiple independent tasks. Instead of splitting the data itself, which is common in parallel processing, we split the list of individual difference variables (e.g., those matching the pattern "\^scMC.\*indv\$"). We create chunks of these variables, distributed across the number of cores - 1. The function `cni.ContMod_effects` function is applied to each variable in `var_names` simultaneously across different cores. Each core processes a different moderator variable independently.

The mindsetCNI models were run on the Talapas (120GB RAM and 30 cores). For the rest of teh CNI types the hardware used involved 64GB RAM and 12 core processor, with the longest processing time for a model being 25mins (1529.822 sec elapsed). A motivated reader may choose to try to optimize this even further, in a more constrained environment.

```{r parallel-processing-contMod, echo = F, eval = F}
# Load necessary libraries
library(furrr)
library(purrr)
library(tictoc)

# Set up parallel processing
plan(multisession, workers = availableCores() - 1)

tic()
# Get the list of moderator variables
patterns <- c("^scP.*indv$", "^scP.*comm$")
var_names <- grep(paste(patterns, collapse = "|"), names(data2), value = TRUE)

#checklist
#1. check if the patterns are correct 
    #["^scM" for mindset moderators; "^scP" for personality moderators]
#2.change the name of the object
#3. change the data_profiles
#4. save the object in Study 2

# Parallel execution using furrr
pty6CNI.pty_effects<- future_map_dfr(var_names, function(var) {
  result <- cni.ContMod_effects(pty6CNI_profiles$self.ctry_profiles, var)
  result$variable <- var  # Add the variable name to the result
  return(result)
}, .progress = TRUE)


# Reset to sequential processing
plan(sequential)
toc()
```

```{r save-cni.ContMod-models, echo = F, eval = F}
#checklist 
#1. change name of the object  
#2. DANGER: change name of the objet being saved
#use the following to save each or collected chunks in the code above
save(pty6CNI.pty_effects,
     file = here("objects/Study2/pty6CNI.pty_effects.Rdata"))
```

```{r load-cni.ContMod-models, echo = F, results='hide'}
# Define a vector of file names
cni.contMod_object_names <- paste0(
  rep(c("mindset", "ism", "globe", "globeEx", "fantc", "mf", "socAx", "pty6"), each = 2),
  "CNI.",
  rep(c("mindset", "pty"), 8),
  "_effects.Rdata")

# Set file paths and set names
filepaths <- here("objects/Study2", cni.contMod_object_names) %>%
  set_names(nm = basename(.) %>% tools::file_path_sans_ext())

# Load all files
all_cni.contMod_effects <- purrr::map(filepaths, ~get(load(.)))

# Assign loaded objects to global environment - important!
purrr::pmap(.l = list(.x = names(all_cni.contMod_effects), .y = all_cni.contMod_effects), .f = ~assign(.x, .y, envir = .GlobalEnv))

# Verify that objects are now in the global environment
#map_lgl(names(files), ~exists(.x, envir = .GlobalEnv))
```

```{r fun.-specify-var-names}
#function to specify the correct variable names for all moderators [Pty + Cog + swb]
specify_var_names <- \(data){
  data %>% 
    mutate(
    modtr = case_when(
      
      #Personality
      str_detect(modtr, "Consc") ~ "Conscientiousness",
      str_detect(modtr, "Hon") ~ "Honesty",
      str_detect(modtr, "Agr") ~ "Agreeableness",
      str_detect(modtr, "Res") ~ "Resilience",
      str_detect(modtr, "Ext") ~ "Extraversion",
      str_detect(modtr, "Vir") ~ "Originality/Virtuosity",
      str_detect(modtr, "Dis") ~ "Disintegration",
      str_detect(modtr, "SocialSelfReg") ~ "Social Self-Regulation",
     str_detect(modtr, "Dynamism") ~ "Social Dynamism",

      
      #Mindset
      
             #Isms
      str_detect(modtr, "Isms_TradRelig") ~ "Traditional Religiousness", 
      str_detect(modtr, "Isms_UnmiSelfInt") ~ "Unmitigated Self-Interest",
      str_detect(modtr, "CommRation") ~ "Communal Rationalism",
      str_detect(modtr, "SubjSpirit") ~ "Subjective Spirituality",
      str_detect(modtr, "IneqAver") ~ "Inequality Aversion",
  
         #GLOBE
      str_detect(modtr, "globe_igc") ~ "InGroup Collectivism",   
      str_detect(modtr, "globe_ic") ~ "Institutional Collectivism", 
      str_detect(modtr, "globe_pf") ~ "Performance/Achievement Orientation",
      str_detect(modtr, "globe_un") ~ "Uncertainty Avoidance", 
      str_detect(modtr, "globe_ge") ~ "Gender Egalitarian",
      str_detect(modtr, "globe_po") ~ "Power Distance",
      str_detect(modtr, "globe_fu") ~ "Future Orientation",
      str_detect(modtr, "globe_ass") ~ "Assertiveness",
      str_detect(modtr, "globe_hu") ~ "Humane Orientation",
    
        #Social Axioms
     str_detect(modtr, "SocAx_Cynicism") ~ "Social Cynicism",
     str_detect(modtr, "SocAx_RewardForApp") ~ "Reward for Application", 
     str_detect(modtr, "SocAx_Complexity") ~ "Social Complexity", 
     str_detect(modtr, "SocAx_FateControl") ~ "Fate Control",
  str_detect(modtr, "SocAx_Religiosity") ~ "Religiosity",
  
      #Moral Foundations
      str_detect(modtr, "MFQ_Harm") ~ "Harm",
      str_detect(modtr, "MFQ_Fairness") ~ "Fairness",
      str_detect(modtr, "MFQ_Loyalty") ~ "Loyalty",
      str_detect(modtr, "MFQ_Authority") ~ "Authority",
      str_detect(modtr, "MFQ_Purity") ~ "Purity",
  
     #Individualism-Collectivism (Gelfland)
  str_detect(modtr, "IndvColl_CollecHori") ~ "Horizontal Collectivism",
  str_detect(modtr, "IndvColl_CollecVert") ~ "Vertical Collectivism",
  str_detect(modtr, "IndvColl_IndivHori") ~ "Horizontal Individualism",
  str_detect(modtr, "IndvColl_IndivVert") ~ "Vertical Individualism",
  
  #Family Values
  str_detect(modtr, "FamValCohesion") ~ "Cohesion",
  str_detect(modtr, "FamValHierarchy") ~ "Hierarchy",
  
  #Schwartz Values
  str_detect(modtr, "Value_SfTran") ~ "Self Transcendence",
    str_detect(modtr, "Value_Consrv") ~ " Conservation",
  str_detect(modtr, "Value_SelfEnh") ~ "Self Enhancement",
  str_detect(modtr, "Value_OpnChg") ~ "Openness to Change",
   
  #Fanaticism
  str_detect(modtr, "fntc") ~ "Fanaticism",
      
  #Materialism
  str_detect(modtr, "Material") ~ "Materialism",
  
  #Machiavellianism
  str_detect(modtr, "Machiaveln") ~ "Machiavellianism",
  
  #Prone to Aggression (Honor)
   str_detect(modtr, "Prone_Aggr") ~ "Prone to Aggression",
  
  #Ethnonationalism
      str_detect(modtr, "Ethnonational") ~ "Ethnonationalism",
  
  #Tightness-Looseness
      str_detect(modtr, "Tightness") ~ "Tightness",
  
  #Amoralism
      str_detect(modtr, "Amoralism") ~ "Amoralism",
  
  #Duke Religiosity Index
    str_detect(modtr, "DRI_OrgRelgAc") ~ "Organizational Religious Activity",
    str_detect(modtr, "DRI_NonOrgRelgAc") ~ "Non-organizational Religious Activity",
    str_detect(modtr, "DRI_IntrnscRelg") ~ "Intrinsic religiosity",
      
    #Civic Multicultural Nationalism
      str_detect(modtr, "CivicMCNational") ~ "Civic Multicultural Nationalism",
  
      TRUE ~ modtr
    )
  ) 
}
```

## Descriptives - Effect size estimates 

```{r overall-ContEst-trends, results='asis', echo=FALSE}
#| tbl-cap: "Descriptive Statistics for Continuos Moderator Effect size Estimates"
library(e1071)

list_rbind(all_cni.contMod_effects, names_to = "model") %>% 
    mutate(level = case_when(
      level == "Community" ~ "Country",
      TRUE ~ level
    ),
    term = case_when(
      term == "z_ctry_response:modtr_score" ~ "Linear",
      term == "z_ctry_response:I(modtr_score^2)" ~ "Quadratic",
      TRUE ~ term
    )) %>% 
  group_by(term, level) %>%
  summarise(
    min = min(estimate),
    max = max(estimate),
    range = max - min,
    kurtosis = e1071::kurtosis(estimate), 
    skew = e1071::skewness(estimate), 
    n = n(),
    mean = mean(estimate),
    sd = sd(estimate),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  select(-term) %>% 
  kable(booktabs = T, 
        escape = F,
        format = "html",
        col.names = c(" ", "min", "max", "range", "kurtosis", "skew", "n", "mean", "sd")) %>%  
   group_rows("Linear effects", 1, 2) %>% 
  group_rows("Quadratic effects", 3, 4) 
```

```{r overall-ContEst-trends-plot, eval = T, echo = F, results='asis'}
#| fig-cap: "Distribution of Continuos Moderator Effect size Estimates"
#| fig-width: 8
#| fig-height: 4

plot_cont_effects <- function(plot_type) {
   base_data <- list_rbind(all_cni.contMod_effects, names_to = "model") %>%
    mutate(level = case_when(
      level == "Community" ~ "Country",
      TRUE ~ level
    ))
  
  plot_data <- switch(plot_type,
    "overall" = base_data,
    "linear" = base_data %>% filter(term == "z_ctry_response:modtr_score"),
    "quadratic" = base_data %>% filter(term == "z_ctry_response:I(modtr_score^2)"),
    stop("Invalid plot type. Use 'overall', 'linear', or 'quadratic'.")
  )
  
  plot <- ggplot(plot_data, aes(x = estimate, y = after_stat(density))) +
    geom_density(color = "grey40", fill = "grey80", alpha = 0.5) +
    geom_density(aes(fill = level, color = level), alpha = 0.5) +
    scale_fill_manual(values = c("Individual" = "cornflowerblue", "Country" = "pink")) +
    scale_color_manual(values = c("Individual" = "cornflowerblue", "Country" = "pink")) +
    scale_x_continuous(limits = c(-0.85, 1)) +
    scale_y_continuous(limits = c(0, 280))+
    theme_bw() +
   labs(x = "Effect size Estimates", y = "Density", fill = "Level", color = "Level")
  
  return(plot)
}

plot_cont_effects("overall") + 
plot_cont_effects("linear") +
plot_cont_effects("quadratic") + 
  plot_layout(
    axis_titles = "collect",
    guides = "collect"
  )  +
  plot_annotation(
    tag_levels = list(c("Overall", "Linear", "Quadratic"))
  ) &
  theme(
    plot.tag.position = c("top"),
    text = element_text(family = "serif", size = 12),legend.position = "bottom")
```




## Tables
```{r cni.contMod-tbl-details}

CNIplot_data_details = tibble(
  mod_names = c(
    "mindsetCNI_plot",
    "ismCNI_plot",
    "globeCNI_plot",
    "globeExCNI_plot",
    "fantcCNI_plot",
    "mfCNI_plot",
    "socAxCNI_plot",
    "pty6CNI_plot"
  ),
  caption = c(
    "Mindset CNI",
    "Isms-Mindset CNI",
    "Globe-Mindset CNI",
    "Globe (Extra items)",
    "Fanaticism-Mindset CNI",
    "Moral Foundations-Mindset CNI",
    "Social Axioms-Mindset CNI",
    "Personality6 CNI"
  )
)


cni.contMod_object_names <- c(
  "mindsetCNI.mindset_effects.Rdata",
  "mindsetCNI.pty_effects.Rdata",
  "ismCNI.mindset_effects.Rdata",
  "ismCNI.pty_effects.Rdata",
  "globeCNI.mindset_effects.Rdata",
  "globeCNI.pty_effects.Rdata",
  "globeExCNI.mindset_effects.Rdata",
  "globeExCNI.pty_effects.Rdata",
  "fantcCNI.mindset_effects.Rdata",
  "fantcCNI.pty_effects.Rdata",
  "mfCNI.mindset_effects.Rdata",
  "mfCNI.pty_effects.Rdata",
  "socAxCNI.mindset_effects.Rdata",
  "socAxCNI.pty_effects.Rdata",
  "pty6CNI.mindset_effects.Rdata",
  "pty6CNI.pty_effects.Rdata"
)

cni.contMod_tbl_details <- tibble(
  object_names = names(all_cni.contMod_effects)) %>%
  mutate(obj_name = str_extract(object_names, "^[^.]+")) %>%
  left_join(
    CNIplot_data_details %>%
      mutate(mod_name = str_remove(mod_names, "_plot$")),
    by = c("obj_name" = "mod_name")) %>%
  select(object_names, caption) %>% 
  mutate(
    CNI_type = case_when(
      str_detect(object_names, ".mindset") ~ "Mindset",
      str_detect(object_names, ".pty") ~ "Personality",
      TRUE ~ NA_character_  # for any cases that don't match either condition
    )) %>%
  mutate(caption = paste0("Associations between ",caption, " and ", CNI_type, " variables")) %>% 
  select(object_names, caption, CNI_type)
```

### Linear and Quadratic effects (CNI)

```{r fun.-cni.ContMod-effects-tbl}
cni.ContMod_effects_table <- \(data, title){
df2 <- data %>% 
    #specify the correct variable/moderator name
    specify_var_names()%>% 
    select(-relation) %>% 
    mutate(
    p.value = map_chr(p.value, papaja::printp),
    across(where(is.numeric), ~ round(., 3)),
  ci = paste0("[", conf.low, ", ", conf.high,"]"),
         term = ifelse(str_detect(term, "2"), "Quadratic", "Linear"),
    estimate = as.character(estimate) 
  ) %>% 
  select(level, modtr, term, estimate, ci, p.value) %>% 
  pivot_longer(cols = c(estimate, ci, p.value),  names_to = "stat", values_to = "stat_value") %>% 
  unite(term, term, stat) %>% 
  pivot_wider(names_from = term, values_from = stat_value) %>% 
  arrange(desc(level)) %>%
  select(-level) %>% 
  select(modtr, contains("Linear"), contains("Quadratic"))

 # Calculate the number of rows for each level
no.modtrs <- df2 %>% 
  distinct(modtr) %>% 
  nrow()

df2 %>% 
  kable(booktabs = T, 
        escape = F,
        format = "latex",
        longtable = TRUE,
        col.names = c(" ", "Est", "95\\% CI", "p", "Est", "95\\% CI", "p"),
        caption = title ) %>%  
  kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
  add_header_above(c(" ", "Linear (b)" = 3, "Quadratic (b^2)" = 3)) %>% 
     group_rows("Individual level", 1, no.modtrs, bold = TRUE, italic = T) %>% 
  group_rows("Country level", no.modtrs+1, no.modtrs*2, bold = TRUE, italic = T) %>%
      column_spec(1, width = "5.5cm")

}
```

```{r cni.MindsetMod-effects-tbl, results='asis'}
#| cache: true
cni.contMod_tbl_details %>% 
  filter(CNI_type == "Mindset") %>%
  pwalk(function(object_names, caption, ...) {
    cat("\n\n")
    print(
      pluck(all_cni.contMod_effects, object_names) %>% 
        cni.ContMod_effects_table(., caption)
    )
    cat("\n\n")
  })
```

```{r cni.PersonalityMod-effects-tbl, results='asis'}
#| cache: true
cni.contMod_tbl_details %>% 
  filter(CNI_type == "Personality") %>%
  pwalk(function(object_names, caption, ...) {
    cat("\n\n")
    print(
      pluck(all_cni.contMod_effects, object_names) %>% 
        cni.ContMod_effects_table(., caption)
    )
    cat("\n\n")
  })
```

### Strongest and Weakest effects (CNI)

```{r eval=FALSE, echo=FALSE, include=FALSE}
quick_strong.weak_effects_table <- function(data, title) {
  
  base_data <- data %>%
    specify_var_names() %>%
    filter(round(p.value, 3) < 0.05) %>%
    arrange(desc(abs(estimate))) %>%
    mutate(
      term_type = case_when(
        term == "z_ctry_response:modtr_score" ~ "Linear",
        term == "z_ctry_response:I(modtr_score^2)" ~ "Quadratic",
        TRUE ~ NA_character_
      )
    )
  
  # Select 15 highest and 15 lowest estimates
  highest_15 <- base_data %>% head(15)
  lowest_15 <- base_data %>% tail(15) %>% 
  arrange(abs(estimate))
  
  # Combine the data using bind_rows with .id argument
  all_data <- bind_rows(list("Highest 15 Estimates" = highest_15, 
                             "Lowest 15 Estimates" = lowest_15), 
                        .id = "group")
  
  # Prepare data for table
  df2 <- all_data %>%
    select(-relation) %>%
    mutate(
      p.value = map_chr(p.value, papaja::printp),
      across(where(is.numeric), ~ round(., 3)),
      ci = paste0("[", conf.low, ", ", conf.high,"]"),
      term = ifelse(str_detect(term, "2"), "(b\\textsuperscript{2})", "(b)"),
      estimate = as.character(estimate),
    modtr = ifelse(level == "Country", 
                   paste0(modtr, footnote_marker_symbol(1, "latex")),
                   paste0(modtr, footnote_marker_symbol(2, "latex")))) %>%
    select(group, modtr, term, estimate, ci, p.value)%>%
    arrange(group) %>% 
    select(-group)
  
  # Create and return the table
  df2 %>%
    kable(booktabs = T,
          escape = F,
          format = "latex",
          longtable = TRUE,
          col.names = c("Moderator", "Term", "Est", "95\\% CI", "$\\textit{p}$" ),
          caption = title) %>%
    group_rows("Strongest 15 Estimates", 1, 15, underline = T, escape = F) %>%
    group_rows("Weakest 15 Estimates", 16, 30, escape = F, underline = T) %>%
    kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
    column_spec(1, width = "6.4cm") %>% 
      footnote(symbol = c("Country level", "Individual level"),
           symbol_title = "",
           general = "(b) = Linear model, ($b\\textsuperscript{2}$) = Quadratic",
           general_title = "Note:",
           title_format = "italic", 
           fixed_small_size = TRUE,
           footnote_as_chunk = FALSE,
           threeparttable = TRUE,
           escape = FALSE)
}

#quick_strong.weak_effects_table(all_cni.contMod_effects$pty6CNI.pty_effects, pull(cni.contMod_tbl_details, "caption2")[16])
```

```{r}
strong.weak_effects_table <- function(data, title) {
  
  base_data <- data %>%
    specify_var_names() %>%
    filter(round(p.value, 3) < 0.05) %>%
    arrange(desc(abs(estimate))) %>%
    mutate(
      term_type = case_when(
        term == "z_ctry_response:modtr_score" ~ "Linear",
        term == "z_ctry_response:I(modtr_score^2)" ~ "Quadratic",
        TRUE ~ NA_character_
      )
    )
  
  # Select 15 highest and 15 lowest estimates
  highest_15 <- base_data %>% head(15)
  lowest_15 <- base_data %>% tail(15) %>% 
  arrange(abs(estimate))
  
  # Combine the data using bind_rows with .id argument
  all_data <- bind_rows(list("Highest 15 Estimates" = highest_15, 
                             "Lowest 15 Estimates" = lowest_15), 
                        .id = "group")
  
  # Prepare data for table
  df2 <- all_data %>%
    select(-relation) %>%
    mutate(
      p.value = map_chr(p.value, papaja::printp),
      across(where(is.numeric), ~ round(., 3)),
      ci = paste0("[", conf.low, ", ", conf.high,"]"),
      term = ifelse(str_detect(term, "2"), "(b\\textsuperscript{2})", "(b)"),
      estimate = as.character(estimate),
    modtr = ifelse(level == "Country", 
                   paste0(modtr, footnote_marker_symbol(1, "latex")),
                   paste0(modtr, footnote_marker_symbol(2, "latex")))) %>%
    select(group, modtr, term, estimate, ci, p.value)%>%
    arrange(group) %>% 
    select(-group)
  
  # Create and return the table
  df2 %>%
    kable(booktabs = T,
          escape = F,
          format = "latex",
          longtable = TRUE,
          col.names = c("Moderator", "Term", "Est", "95\\% CI", "$\\textit{p}$" ),
          caption = title) %>%
    group_rows("Strongest 15 Estimates", 1, 15, underline = T, escape = F) %>%
    group_rows("Weakest 15 Estimates", 16, 30, escape = F, underline = T) %>%
    kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
    column_spec(1, width = "6.4cm") %>% 
      footnote(symbol = c("Country level", "Individual level"),
           symbol_title = "",
           general = "(b) = Linear model, ($b\\textsuperscript{2}$) = Quadratic",
           general_title = "Note:",
           title_format = "italic", 
           fixed_small_size = TRUE,
           footnote_as_chunk = FALSE,
           threeparttable = TRUE,
           escape = FALSE)
}

cni.contMod_tbl_details <- cni.contMod_tbl_details %>%
    mutate(caption2 = paste0("Strongest and Weakest ", caption))
```

```{r cni.contMod-strong.weak-effects-tbl, results='asis'}
#| cache: true
cni.contMod_tbl_details %>% 
  select(-caption) %>% 
  pwalk(function(object_names, caption2, ...) {
    cat("\n\n")
    print(
      pluck(all_cni.contMod_effects, object_names) %>% 
        strong.weak_effects_table(., caption2)
    )
    cat("\n\n")
  })
```

### Five Strongest moderators

```{r five-strongest-moderators}
cni_types <- unique(sub("CNI.*", "CNI", names(all_cni.contMod_effects)))

# Function to combine dataframes for a given CNI type
#data_list = all_cni.contMod_effects
strongest5_contMods <- function(cni_type, data_list) {
  df_names <- grep(paste0("^", cni_type),
                   names(data_list), value = TRUE)
  
  bind_rows(data_list[df_names], .id = "modtr_type") %>%
    arrange(desc(abs(estimate))) %>%
    slice_head(n = 5)
}

# Apply the function to each CNI type
strongest5_contMods_CNI <- map_dfr(cni_types, ~strongest5_contMods(.x, all_cni.contMod_effects)) %>%
  specify_var_names() %>% 
  with_groups(modtr, ~ mutate(.x, avg_abs_estimate = mean(abs(estimate)))) %>% 
  mutate(modtr = fct_reorder(modtr, avg_abs_estimate, .desc = FALSE)) %>% 
  select(-term, -variable)  %>% 
  mutate(cni_type = str_extract(modtr_type, "^[^.]+")) %>% 
  mutate(label_color = case_when(
    str_detect(modtr_type, "\\.pty_effects$") ~ "#c76e00",
    str_detect(modtr_type, "\\.mindset_effects$") ~ "#008000",
    TRUE ~ "black"
  ))

modtr_order <- strongest5_contMods_CNI %>%
  group_by(modtr) %>%
  summarize(mean_estimate = mean(estimate)) %>%
  arrange(mean_estimate) %>%
  pull(modtr)


strongest5_contMods_CNI <- strongest5_contMods_CNI %>%
  mutate(modtr = factor(modtr, levels = modtr_order))


color_mapping <- strongest5_contMods_CNI %>%
  select(modtr, label_color) %>%
  distinct() %>%
  deframe()
```

```{r results='asis'}
#| fig-height: 7
#| fig-width: 10
#| out-width: "100%"
#| cap-location: bottom
#| fig-cap: "Five Strongest Estimates across CNI types"

strongest5_contMods_CNI %>% 
 ggplot(aes(x = modtr, y = estimate, color = cni_type, group = interaction(modtr))) +
   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, alpha = 0.3, size = 3.8, position = position_dodge(width = 0.4), linetype = "solid")+
   geom_point() + 
  scale_color_manual(values = c("mindsetCNI" = "#0074B7", "ismCNI"  = "#6082B6", "fantcCNI"  = "#70d6ff", "globeCNI"  = "#a0c4ff", "globeExCNI"  = "#189AB4", "mfCNI"  = "#6495ED", "socAxCNI"  = "#5D3FD3", "pty6CNI" = "#ff70a6")) +
   labs(x = NULL, 
        y = "CNI estimate",
        color = "CNI Types",  
        caption = "<i>Note:</i> <span style='color:#c76e00;'>Personality </span> and <span style='color:#008000;'>Mindset </span> moderators on Y axis") +
   coord_flip() +
   theme_bw() +
   theme(plot.title.position = "plot", 
         text = element_text(family = "serif", size = 12),
      axis.text.y = element_markdown(
      color = color_mapping[levels(strongest5_contMods_CNI$modtr)],
      size = 12),
      plot.caption = element_markdown(hjust =1.74, size = 8.3) )
```

```{r}
#| include: false
#knitr::opts_chunk$set(eval = FALSE)
```

### Overall trends

Similar to study 1, three categories of tables are presented here: 1. Strongest moderators: Effects that significantly enhance or diminish the impact of cultural normativity. 2. Weakest moderators: Effects that, while statistically significant, have minimal influence on cultural normativity. 3. Non-significant effects: Factors that show no statistically significant moderation of cultural normativity.

```{r fun.-overall-effects-table}
overall_table <- function(table_type, title) {
  table <- bind_rows(all_cni.contMod_effects, .id = "model") 
  
  if (table_type == "overall highest") {
    table <- table %>%
      filter(p.value < .05) %>%
      arrange(desc(abs(estimate)))
  } else if (table_type == "overall weakest") {
    table <- table %>%
      filter(p.value < .05) %>%
      arrange(abs(estimate))
  } else if (table_type == "overall n.s") {
    table <- table %>%
      filter(p.value >= .05) %>%
      arrange(abs(estimate))
  } else {
    stop("Invalid table_type. Choose 'overall highest', 'overall lowest', or 'overall n.s'")
  }

final_table <- table %>%
  head(20) %>%
  specify_var_names() %>% 
  separate(model, c("CNI_type", "Moderator_type"), sep = "\\.") %>%
  mutate(
    CNI_type = str_remove(CNI_type, "CNI"),
    CNI_type = str_to_sentence(CNI_type),
    CNI_type = str_replace_all(CNI_type, c( 
      "cni" = " CNI",
      "Ism" = "Isms",
      "Fantc" = "Fanaticism",
      "Globe" = "GLOBE", 
      "Pty6" = "Personality 6",
      "Pty7" = "Personality 7")),
    Moderator_type = if_else(Moderator_type == "pty7", "Personality", "Mindset"),
    p.value = map_chr(p.value, papaja::printp),
    across(where(is.numeric), ~ round(., 3)),
    ci = paste0("[", conf.low, ", ", conf.high,"]"),
    term = ifelse(str_detect(term, "2"), "(b\\textsuperscript{2})", "(b)"),
    estimate = as.character(estimate),
    modtr = paste0(modtr, " (", Moderator_type, ")"),
    modtr = ifelse(level == "Country", 
                   paste0(modtr, footnote_marker_symbol(1, "latex")),
                   paste0(modtr, footnote_marker_symbol(2, "latex"))
    ),
    CNI_type = str_replace(CNI_type, "CNI", "")
  ) %>% 
  select(CNI_type, modtr, term, estimate, ci, p.value)

final_table %>% 
  kable(booktabs = T, 
        escape = F,
        format = "html",
        col.names = c("CNI type", "Moderator", "Term", "Est", "95\\% CI", "$\\textit{p}$"),
        caption = title,
        longtable = T) %>% 
  kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
  footnote(symbol = c("Country", "Individual"),
           symbol_title = "",
           general = "(b) = Linear model, (b\\textsuperscript{2}) = Quadratic",
           general_title = "Note:",
           title_format = "italic", 
           fixed_small_size = TRUE,
           footnote_as_chunk = FALSE,
           threeparttable = TRUE,
           escape = FALSE)
}

overall_table_details <- tibble(
  table_type = c("overall highest", "overall weakest", "overall n.s"))%>% 
  mutate(title = paste0("Variables with ", word(table_type , 2), " effect sizes with each CNI type"))
```

```{r overall-effects-table, echo = F, results='asis'}
#|cache: true
overall_table_details %>%
  pwalk(function(table_type, title) {
    cat("\n\n")
    print(overall_table(table_type, title))
    cat("\n\n")
  })
```

## Plots

### Strongest and Weakest effects (CNI)

Given that there are `r (length(str_subset(names(data2), "\\.(indv|comm)$"))-1)*2` (individual level scale scores = `r (length(str_subset(names(data2), "\\.(indv)$")))-1`, country level scale scores = `r (length(str_subset(names(data2), "\\.(comm)$")))-1` and their linear and quadratic associations with CNI types) effect sizes to evaluate in total for each CNI type, it was necessary to identify a starting point. In order to assess the continuous moderator effects for each of the CNI types, the highest 15 and lowest 15 associations (across linear and quadratic) were considered.

```{r fun.plot-high-low-effects}
plot_high.low_mindset_effects <- function(data) {

  base_data <- data %>%
    specify_var_names() %>%
    filter(round(p.value, 3) < 0.05) %>% #distinct(level) %>%
    arrange(desc(abs(estimate))) %>% 
    mutate(
     color = case_when(
        str_detect(variable, "MFQ") ~ "Moral Foundations",
        str_detect(variable, "SocAx") ~ "Social Axioms",
        str_detect(variable, "globe") ~ "Globe",
        str_detect(variable, "Isms|CommRation|SubjSpirit|IneqAver") ~ "Isms",
        str_detect(variable, "IndvColl") ~ "Individualism-Collectivism",
        str_detect(variable, "FamVal") ~ "Family Values",
        str_detect(variable, "Value") ~ "Schwartz Values",
        str_detect(variable, "fntc") ~ "Fanaticism",
        str_detect(variable, "Material") ~ "Materialism",
        str_detect(variable, "Machiaveln") ~ "Machiavellianism",
        str_detect(variable, "Prone_Aggr") ~ "Prone to Aggression",
        str_detect(variable, "Ethnonational") ~ "Ethnonationalism",
        str_detect(variable, "Tightness") ~ "Tightness-Looseness",
        str_detect(variable, "Amoralism") ~ "Amoralism",
        str_detect(variable, "DRI") ~ "Duke Religiosity Index",
        str_detect(variable, "CivicMCNational") ~ "Civic Multicultural Nationalism",
        TRUE ~ "OTHER"),
      term_type = case_when(
  term == "z_ctry_response:modtr_score" ~ "Linear",
  term == "z_ctry_response:I(modtr_score^2)" ~ "Quadratic",
  TRUE ~ NA_character_, 
        .default = NA_character_)
    )
  
  # Select 15 highest and 15 lowest estimates and tag them as 'Highest' or 'Lowest'
  highest_15 <- base_data %>% head(15) %>% mutate(group = "Highest 15 Estimates")
  lowest_15 <- base_data %>% tail(15) %>% mutate(group = "Lowest 15 Estimates")
  
  # Combine the data
  all_data <- bind_rows(highest_15, lowest_15)

  # Define the overall range of estimates for consistent axis scaling
  estimate_range <- range(c(all_data$conf.high, all_data$conf.low))

  # Define the plot
  combined_plot <- ggplot(all_data, 
    aes(x = reorder(modtr, estimate), y = estimate, color = color, linetype = term_type, shape = level, group = interaction(modtr, term_type, level))) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, alpha = 0.3, size = 3, position = position_dodge(width = 0.4), linetype = "solid") +
    
    geom_point(size = 2, position = position_dodge(width = 0.4)) +
    
    geom_linerange(aes(ymin = 0, ymax = estimate), position = position_dodge(width = 0.4)) +
    
    scale_shape_manual(values = c("Country" = 15, "Individual" = 17), drop = FALSE) +
   scale_color_manual(values = c(
  "Isms" = "#7F0000",
  "Globe" = "#377EB8",
  "Social Axioms" = "#4DAF4A",
  "Moral Foundations" = "#984EA3",
  "Individualism-Collectivism" = "#FF7F00",
  "Family Values" = "#DAA520",
  "Schwartz Values" = "#5A3CB4",
  "Fanaticism" = "#196569",
  "Materialism" = "#F781BF",
  "Machiavellianism" = "#8f8d2f",
  "Prone to Aggression" = "#E41A1C",
  "Ethnonationalism" = "#C67B53",
  "Tightness-Looseness" = "#8B4513",
  "Amoralism" = "#00FFFF",
  "Duke Religiosity Index" = "#FF1493",
  "Civic Multicultural Nationalism" = "#1da87e"
), drop = FALSE) +
    scale_linetype_manual(values = c("Linear" = "dotdash", "Quadratic" = "solid"), drop = FALSE) +
    scale_y_continuous(limits = estimate_range) +  
    coord_flip() +
    facet_wrap(~group, ncol = 1, scales = "free_y")+
    theme_minimal(base_family = "serif", base_size = 12) +
    labs(
      x = NULL,
      y = "Estimate",
      color = "Domain",
      shape = "Level",
      linetype = "Association") +
            theme_bw() +
    theme(text = element_text(family = "serif", size = 12), legend.position = "bottom",
           legend.text = element_text(size = 8.1), 
      legend.title = element_text(size = 8.5))+

    guides(
  color = guide_legend(ncol = 4, title.position = "top"),  # 2 columns for Domain
  shape = guide_legend(ncol = 1, title.position = "top"),  # 1 column for Level
  linetype = guide_legend(ncol = 1, title.position = "top")  # 1 column for Association
)

  return(combined_plot)
}

plot_high.low_pty_effects <- function(data) {
  base_data <- data %>%
   # cni.ContMod_tables$ismCNI.pty %>% 
    specify_var_names() %>%
    filter(round(p.value, 3) < 0.05) %>%
    arrange(desc(abs(estimate))) %>%
    mutate(
     color = case_when(
      modtr == "Conscientiousness" ~ "Big 6",
      modtr == "Honesty" ~ "Big 6",
      modtr == "Agreeableness" ~ "Big 6",
      modtr == "Resilience" ~ "Big 6",
      modtr == "Extraversion" ~ "Big 6",
      modtr == "Originality/Virtuosity" ~ "Big 6",
      modtr == "Social Self-Regulation"~ "Big 2",
      modtr == "Social Dynamism"~ "Big 2",
      TRUE ~ "Other"),
      term_type = case_when(
        term == "z_ctry_response:modtr_score" ~ "Linear",
        term == "z_ctry_response:I(modtr_score^2)" ~ "Quadratic",
        TRUE ~ NA_character_, 
        .default = NA_character_)
    )
  
  # Select 15 highest and 15 lowest estimates and tag them as 'Highest' or 'Lowest'
  highest_15 <- base_data %>% head(15) %>% mutate(group = "Highest 15 Estimates")
  lowest_15 <- base_data %>% tail(15) %>% mutate(group = "Lowest 15 Estimates")
  
  # Combine the data
  all_data <- bind_rows(highest_15, lowest_15)
  # Define the overall range of estimates for consistent axis scaling
  estimate_range <- range(c(all_data$conf.low, all_data$conf.high))
  
  # Define the plot
  combined_plot <- ggplot(all_data, 
    aes(x = reorder(modtr, estimate), y = estimate, color = color, linetype = term_type, shape = level, group = interaction(modtr, term_type, level))) +
   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, alpha = 0.3, size = 3, position = position_dodge(width = 0.4), stat = "identity", linetype = "solid") +
    
    geom_point(aes(shape = level), size = 2, position = position_dodge(width = 0.4)) +
    
    geom_linerange(aes(ymin = 0, ymax = estimate, linetype = term_type), position = position_dodge(width = 0.4)) +
    
    scale_shape_manual(values = c("Country" = 15, "Individual" = 17), drop = FALSE) +
    scale_color_manual(values = c(
   "Big 2" = "#377EB8",
  "Big 6" = "#008f7a")) +
    scale_linetype_manual(values = c("Linear" = "dotdash", "Quadratic" = "solid"), drop = FALSE) +
    scale_y_continuous(limits = estimate_range) +  # Ensure consistent y-axis limits
    coord_flip() +
    facet_wrap(~group, ncol = 1, scales = "free_y") +  # Facet the plot into Highest and Lowest
    theme_minimal(base_family = "serif", base_size = 12) +
    labs(
      x = NULL,
      y = "Estimate",
      color = "Domain",
      fill = "Domain",
      shape = "Level",
      linetype = "Association") +
    theme_bw() +
    theme(
      text = element_text(family = "serif", size = 12), legend.position = "bottom")  +

    guides(
      color = guide_legend(ncol = 2, title.position = "top"),  # 2 columns for Domain
      fill = guide_legend(ncol = 2, title.position = "top"),  # 2 columns for Domain (for the ribbon)
      shape = guide_legend(ncol = 1, title.position = "top"),  # 1 column for Level
      linetype = guide_legend(ncol = 1, title.position = "top")  # 1 column for Association
    )
  
  return(combined_plot)
}

```

```{r echo=F}
#| fig-height: 10
#| fig-width: 7
#| out-width: "100%"
#| fig-cap-location: bottom
#| fig-cap: !expr |-
#|   cni.contMod_tbl_details %>%
#|     filter(CNI_type == "Mindset") %>%
#|     mutate(caption = paste0("Overall trends: ", 
#|                             str_extract(caption, "Associations.*"))) %>%
#|     pull(caption)

cni.contMod_tbl_details %>% 
  filter(CNI_type == "Mindset") %>%
  pull(object_names) %>%
  walk(~ {
    cat("\n\n")
    # Extract the table and generate the plot
    table_data <- pluck(all_cni.contMod_effects, .x )
    plot <- 
      plot_high.low_mindset_effects(table_data)

    print(plot)
    cat("\n\n")
  })
```

```{r echo=F}
#| fig-height: 8
#| fig-width: 7
#| out-width: "100%"
#| fig-cap-location: bottom
#| fig-cap: !expr |
#|   cni.contMod_tbl_details %>%
#|     filter(CNI_type == "Personality") %>%
#|     mutate(caption = paste0("Overall trends: ", str_extract(caption, "Associations.*"))) %>%
#|     pull(caption)

 

cni.contMod_tbl_details %>% 
  filter(CNI_type == "Personality") %>%
  pull(object_names) %>%
  walk(~ {
    cat("\n\n")
    # Extract the table and generate the plot
    table_data <- pluck(all_cni.contMod_effects, .x )
    plot <- 
      plot_high.low_pty_effects(table_data)
    
    # Print the plot
    print(plot)
    cat("\n\n")
  })
```

### Linear and Quadratic effects

```{r fun.-cni.ContMod-effects-plot}
cni.pty_effects_plot <-\(data, association_type){

  if (association_type == "linear") {
    data_ass.type <- data %>% #cni.ContMod_tables$globeCNI.pty7
      #linear effects
      filter(term == "z_ctry_response:modtr_score")
  } else if (association_type == "quadratic") {
    data_ass.type <- data %>% 
      #quadratic effects
      filter(term == "z_ctry_response:I(modtr_score^2)")
  } else {
    stop("Invalid association type. Choose 'linear' or 'quadratic'")
  }
   
processed_data <-  data_ass.type %>%  
  specify_var_names() %>%
  with_groups(modtr, ~ mutate(.x, avg_abs_estimate = mean(abs(estimate)))) %>% 
  mutate(
    modtr = fct_reorder(modtr, avg_abs_estimate, .desc = FALSE),
    domain = case_when(
      modtr == "Conscientiousness" ~ "Big 6",
      modtr == "Honesty" ~ "Big 6",
      modtr == "Agreeableness" ~ "Big 6",
      modtr == "Resilience" ~ "Big 6",
      modtr == "Extraversion" ~ "Big 6",
      modtr == "Originality/Virtuosity" ~ "Big 6",
      modtr == "Social Self-Regulation"~ "Big 2",
      modtr == "Social Dynamism"~ "Big 2",
      TRUE ~ "Other"),
    sig = case_when(
      p.value < .05 & estimate > 0 ~ "Pos",
      p.value < .05 & estimate < 0 ~ "Neg",
      TRUE ~ "NOT"),
      colors = case_when(
  domain == "Big 2" ~ "#377EB8",
   domain == "Big 6" ~ "#008f7a")
  )


 base_plot <- ggplot(processed_data, aes(x = modtr, y = estimate, fill = domain, alpha = level)) +
  geom_col(position = position_dodge(width = 0.8)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                position = position_dodge(width = 0.8),
                width = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
 scale_fill_manual(values = setNames(processed_data$colors, processed_data$domain)) +
  scale_alpha_manual(values = c("Individual" = 1, "Country" = 0.4)) +
  labs(x = "Moderator", y = "Estimate",
       fill = "Trait", alpha = "Level") 

    get_color_mapping <- function(data) {
  data %>%
    arrange(desc(avg_abs_estimate)) %>%
    distinct(modtr, .keep_all = TRUE) %>%
    select(modtr, colors) %>%
    deframe()
}

# Get the color mapping
color_mapping <- get_color_mapping(processed_data)

 final_plot <- base_plot +
       # domain independent order
    theme_bw() +
    coord_flip()+
  theme(text = element_text(family="serif", size = 11),
    legend.position = "bottom",
    axis.text.y = element_markdown(
      color = color_mapping[levels(processed_data$modtr)],
      size = 11))
     
     return(final_plot)
}


cni.mindset_effects_plot <- function(data, association_type, plot_type = c("domain dependent", "domain independent")) {
  
  if (association_type == "linear") {
    data_ass.type <- data %>% 
      #linear effects
      filter(term == "z_ctry_response:modtr_score")
  } else if (association_type == "quadratic") {
    data_ass.type <- data %>% 
      #quadratic effects
      filter(term == "z_ctry_response:I(modtr_score^2)")
  } else {
    stop("Invalid association type. Choose 'linear' or 'quadratic'")
  }
   
processed_data <-  data_ass.type %>%  
    specify_var_names() %>%
    with_groups(modtr, ~ mutate(.x, avg_abs_estimate = mean(abs(estimate)))) %>% 
    mutate(
      modtr = fct_reorder(modtr, avg_abs_estimate, .desc = FALSE),
      domain = case_when(
        str_detect(variable, "MFQ") ~ "Moral Foundations",
        str_detect(variable, "SocAx") ~ "Social Axioms",
        str_detect(variable, "globe") ~ "Globe",
        str_detect(variable, "Isms|CommRation|SubjSpirit|IneqAver") ~ "Isms",
        str_detect(variable, "IndvColl") ~ "Individualism-Collectivism",
        str_detect(variable, "FamVal") ~ "Family Values",
        str_detect(variable, "Value") ~ "Schwartz Values",
        str_detect(variable, "fntc") ~ "Fanaticism",
        str_detect(variable, "Material") ~ "Materialism",
        str_detect(variable, "Machiaveln") ~ "Machiavellianism",
        str_detect(variable, "Prone_Aggr") ~ "Prone to Aggression",
        str_detect(variable, "Ethnonational") ~ "Ethnonationalism",
        str_detect(variable, "Tightness") ~ "Tightness-Looseness",
        str_detect(variable, "Amoralism") ~ "Amoralism",
        str_detect(variable, "DRI") ~ "Duke Religiosity Index",
        str_detect(variable, "CivicMCNational") ~ "Civic Multicultural Nationalism",
        TRUE ~ "OTHER"),
      sig = case_when(
        p.value < .05 & estimate > 0 ~ "Pos",
        p.value < .05 & estimate < 0 ~ "Neg",
        TRUE ~ "NOT")
    ) %>% 
    mutate(
      colors = case_when(
        str_detect(domain, "Isms") ~ "#7F0000",
        str_detect(domain, "Globe") ~ "#377EB8",
        str_detect(domain, "Social Axioms") ~ "#4DAF4A",
        str_detect(domain, "Moral Foundations") ~ "#984EA3",
        str_detect(domain, "Individualism-Collectivism") ~ "#FF7F00",
        str_detect(domain, "Family Values") ~ "#DAA520",
        str_detect(domain, "Schwartz Values") ~ "#5A3CB4",
        str_detect(domain, "Fanaticism") ~ "#196569",
        str_detect(domain, "Materialism") ~ "#F781BF",
        str_detect(domain, "Machiavellianism") ~ "#8f8d2f",
        str_detect(domain, "Prone to Aggression") ~ "#E41A1C",
        str_detect(domain, "Ethnonationalism") ~ "#C67B53",
        str_detect(domain, "Tightness-Looseness") ~ "#8B4513",
        str_detect(domain, "Amoralism") ~ "#00FFFF",
        str_detect(domain, "Duke Religiosity Index") ~ "#FF1493",
        str_detect(domain, "Civic Multicultural Nationalism") ~ "#1da87e",
        TRUE ~ "#000000"
      )
    )

  base_plot <- ggplot(processed_data, aes(x = modtr, y = estimate, fill = domain, alpha = level)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(width = 0.8), width = 0.25) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    scale_fill_manual(
  values = setNames(processed_data$colors, processed_data$domain),
  guide = guide_legend(
    position = "bottom",
    ncol = 4,
    direction = "vertical"))  +
    scale_alpha_manual(
  values = c("Individual" = 1, "Country" = 0.4),
  guide = guide_legend(
    position = "bottom",
    ncol = 1,
    direction = "vertical")) +
    labs(x = NULL, y = "Estimate", fill = "Trait", alpha = "Level")
  
    #add here different plot versions
    
  if(plot_type=="domain dependent"){
    final_plot <- base_plot +
      labs(caption = paste(tools::toTitleCase(plot_type), "view"))+
        #domain dependent order
   scale_x_discrete(
    limits = unique(processed_data$modtr),
    labels = function(x) {
      sapply(x, function(label) {
        color <- processed_data$colors[processed_data$modtr == label][1]
        sprintf("<span style='color: %s'>%s</span>", color, label)
      })
    }
  ) +
  theme_bw() +
  theme(axis.text.y = element_markdown(size = 11), 
  text = element_text(family="serif", size = 10)) +
  coord_flip()
  }else if(plot_type=="domain independent"){
    
    get_color_mapping <- function(data) {
  data %>%
    arrange(desc(avg_abs_estimate)) %>%
    distinct(modtr, .keep_all = TRUE) %>%
    select(modtr, colors) %>%
    deframe()
}

# Get the color mapping
color_mapping <- get_color_mapping(processed_data)

     final_plot <- base_plot +
      labs(caption = paste(toTitleCase(plot_type), "view"))+
       # domain independent order
    theme_bw() +
    coord_flip()+
  theme(text = element_text(family="serif", size = 10),
    axis.text.y = element_markdown(size = 11,
      color = color_mapping[levels(processed_data$modtr)]
    ))
  }else{
    stop("Invalid plot type. Choose either 'domain dependent' or 'domain independent'.")
  }
return(final_plot)

}


cni.contMod_plot_details <- 
 cni.contMod_tbl_details %>%
  split(.$CNI_type) %>%
  map_dfr(~ {
    if (first(.x$CNI_type) == "Mindset") {
      crossing(.x, 
               view = c("Domain Independent", "Domain Dependent"),
               association_type = c("Linear", "Quadratic"))
    } else if (first(.x$CNI_type) == "Personality") {
      crossing(.x, 
               association_type = c("Linear", "Quadratic")) %>%
        mutate(view = NA_character_)
    } else {
      # For any other CNI_type, keep rows as is
      .x %>% mutate(view = NA_character_, association_type = NA_character_)
    }
  }) 
  

```

```{r walk-cni.mindsetContMod-effects-plot, results='asis', echo=FALSE}
#| cache: true
#| fig-height: 14
#| fig-width: 10
#| out-width: "100%"
#| cap-location: bottom
#| fig-cap: !expr |
#|   cni.contMod_plot_details %>%
#|     filter(CNI_type == "Mindset") %>%
#|     mutate(caption = paste0(view, " view for ", association_type, " effects: ", caption)) %>%
#|     pull(caption)


cni.contMod_plot_details %>%
  filter(CNI_type == "Mindset") %>% 
  mutate(across(c(view, association_type), str_to_lower)) %>%
  select(object_names, association_type, view) %>% 
  pwalk(function(object_names, association_type, view) {
    cat("\n\n")
    print(
      pluck(all_cni.contMod_effects, object_names) %>% 
        cni.mindset_effects_plot(association_type, view)
    )
    cat("\n\n")
  })
```

```{r walk-cni.ptyContMod-effects-plot, results='asis', echo=FALSE}
#| cache: true
#| fig-height: 6
#| fig-width: 10
#| out-width: "100%"
#| cap-location: bottom
#| fig-cap: !expr |
#|   cni.contMod_plot_details %>%
#|     filter(CNI_type == "Personality") %>%
#|     mutate(caption = paste0(association_type, " effects: ", caption)) %>%
#|     pull(caption)

#retain models that have cognitive moderators
cni.contMod_plot_details %>% 
  filter(CNI_type == "Personality") %>%
   mutate(across(c(association_type), str_to_lower)) %>%
  select(object_names, association_type) %>% 
  pwalk(function(object_names, association_type) {
    cat("\n\n")
    print(
      pluck(all_cni.contMod_effects, object_names) %>% 
        cni.pty_effects_plot(association_type)
    )
    cat("\n\n")
  })
```

# RQ 3: To what extent is CNI related to person characteristics?

The primary goal is to assess whether and how specific categorical moderators (modtr_cat) influence the alignment between individual psychological responses (z_response) and country-level psychological profiles (z_ctry_response). The focus is on examining whether the relationship between `z_response` and `z_ctry_response` (i.e., the slope of `z_ctry_response`) changes depending on the level of `modtr_score`. By including the interaction term `z_ctry_response * modtr_score` in the model, the effect of `z_ctry_response` on `z_response` is allowed to vary across different levels of `modtr_score`.

By modeling this relationship, the aim is to:

-   Determine if the degree of cultural normativity varies across levels of the moderator.
-   Understand the interaction between individual and cultural profiles in the context of the moderator.
-   Identify significant factors that contribute to variations in CNI.

*Model fit* is assessed using `car::Anova` wherein the significance of the interaction and the overall model is of interest. Type III sum of squares (focus is on the extent to which the moderator interaction explains variability in the model, above and beyond other main and random effects; Type III is invariant to order effects unlike Type I and accounts for interaction effects unlike Type II). The significant contrasts for each model are retained.

*Marginal effects* or *trends* (slopes) were estimated, adjusted for other variables in the model. This is especially useful when dealing with interactions where direct interpretation of coefficients can be challenging. The `emtrends()` function calculates the estimated slopes of `z_ctry_response` at each level of `modtr_score`, adjusting for other variables in the model (here,`overall.M`) and accounting for the random effects. By specifying `pairwise ~ modtr_score`, pairwise comparisons of these slopes between different levels of `modtr_score` are computed., The `adjust = "holm"` argument ensures that the p-values for these pairwise comparisons are adjusted to reduce the chance of Type I errors due to multiple testing (multiple comparisons adjustment).

## Tables - All differences

```{r table_catMods, echo=FALSE, eval=FALSE}
df <- data.frame(
  `models` = c(
     paste0(c("Mindset", "Isms", "Globe", "Globe (Extra items)", "Fanaticism", "Moral Foundations", "Social Axioms", "Personality 6"), " CNI <- ", c("Sex", "Family Home", "Mother's education", "Father's education", "Age group"))
 ))

table_catMods <- kable(df, format = "latex", align = c("l", "l")) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(1, italic = TRUE) %>%
  add_header_above(c(" " = 2), bold = TRUE)
```

Mindset CNI being the most complex model, it required a different approach for running parallel processing. Here the models are computed first followed by assesing the contrasts between different groups.

```{r mindsetCNI.catMod-models}
cni.CatMod_effects_models <- function(cni_profiles_data, modtr_cat) {
  
  #consists of self,ctry and overall.M profiles
  joined_profiles <- pluck(cni_profiles_data, "self.ctry_profiles") %>%
  left_join(pluck(cni_profiles_data, "overallM_profiles"), by = "item")

  #right data format
  cni.modtr_data <- data2 %>% 
    #select moderator scales individual level (pID) scores 
    select(pID, modtr_cat) %>% 
    pivot_longer(-pID, 
                 names_to = "modtr", #moderator name
                 values_to = "modtr_score") %>% # moderator score
    full_join(joined_profiles, by = c("pID"), relationship = "many-to-many")
  
  #CNI <- moderator
  cni.modtr_model <- cni.modtr_data %>%
      #cni ~ mod [linear]
      lmer(z_response ~ z_ctry_response * modtr_score + overall.M + (-1 + z_ctry_response | pID), data = .)
  
  return(cni.modtr_model)
}
```

```{r parallel-processing-mindsetCNI.catMod, echo = F, eval = F}
# Hardware used: (12-1) cores, 62GB RAM

library(furrr);library(purrr);library(tictoc)
library(car)
emm_options(pbkrtest.limit = 521388) #emtrends setting

# Set up cores
  plan(multisession, workers = availableCores() - 1)

tic()
# All categorical moderator variables
  var_names <- c("sex", "age_group",
                 "mother_edu","father_edu",
                 "family_home")

# Parallel execution using furrr
  mindsetCNI.CatMod_effects_models<- future_map(var_names, function(var) {
    result <- cni.CatMod_effects_models(mindsetCNI_profiles, var)
    return(result)
  }, .progress = TRUE) %>% 
    set_names(var_names)
  
  mindsetCNI.CatMod_effects_models$father_edu %>% #object.size()
    tidy() %>% 
    object.size()


# Reset to sequential processing
plan(sequential)
toc()

#object diagnostics:
  #library(pryr)
  #rm(globeExCNI.cat_effects)
  #object_size(fantcCNI.cat_effects)
  #object_size(globeExCNI.cat_effects$father_edu)
```

```{r save-mindset.cni.CatMod-models, echo = F, eval = F}
#checklist 
#1. change name of the object  
#2. DANGER: change name of the object being saved
#use the following to save each or collected chunks in the code above
save(mindsetCNI.CatMod_effects_models,
     file = here("objects/Study2/mindsetCNI.CatMod_effects_models.Rdata"))
```

```{r echo = F}
load("~/Desktop/CNI_Dissertation/objects/Study2/mindsetCNI.CatMod_effects_models.Rdata")
```


The focus here is to understand how the relationship between `z_ctry_response` and `z_response` changes across different levels of `modtr_score`. Slopes of z_response with respect to z_ctry_response at different values of modtr_score are computed. `emtrends()` from the `emmeans` package is used to compute estimated marginal means (EMMs) of trends. The p-values for multiple comparisons are adjusted using Holm's method. The limit for the parametric bootstrap Kenward-Roger method is increased here.

```{r mindsetCNI.catMod-trends, message=FALSE, warning=FALSE, eval=FALSE, echo=TRUE}
#emm_options(pbkrtest.limit = 1623160)
cni.CatMod_effects_trends <- \(cni.modtr_model) {

   #2. contrasts
  trends <- emtrends(cni.modtr_model, pairwise ~ modtr_score,
  var = "z_ctry_response",
  adjust = "holm")
  
  return(trends)
}

mindsetCNI.CatMod_effects_trends <- map(mindsetCNI.CatMod_effects_models, cni.CatMod_effects_trends)
```

```{r save-mindsetCNI.catMod-trends, eval=FALSE, echo=FALSE}
save(mindsetCNI.CatMod_effects_trends, file = here("objects/Study2/mindsetCNI.CatMod_effects_trends.Rdata"))
```

```{r load-mindsetCNI.catMod-trends, echo = F}
load("~/Desktop/CNI_Dissertation/objects/Study2/mindsetCNI.CatMod_effects_trends.Rdata")
```

```{r fun.-sig_groups1-contrasts, echo = FALSE}
sig_groups1 <- \(df, var, cni_name, sig.only = FALSE) {

  # Extract the part of cni_name before the first period
  cni_name_cap <- str_extract(cni_name, "^[^.]+")
  #age_group -> "Age group"
  var_name_cap <- var %>%
    str_replace_all("_", " ") %>%
    str_to_title()

    trends <- df %>% 
      pluck(var, "contrasts") %>% 
      as.data.frame()
 
  
if (sig.only) {
    trends <- filter(trends, p.value < .05)
    cap <- paste0("Significant differences in ", cni_name_cap, " by ", var_name_cap, ".")
  } else {
    cap <- paste0("Differences in ", cni_name_cap , " by ", var_name_cap, ".")
  }
  
  if (nrow(trends) > 0) {
    trends %>% 
      mutate(
        p.value = papaja::printp(p.value),
        across(where(is.numeric), printnum)
      ) %>% 
      select(-df) %>% 
      kable(booktabs = T,
            caption = cap,
            longtable = T,
            format = "latex",
             col.names = c("Contrast", "Est", "SE", "Z", "p")) %>% 
      kable_styling(latex_options = c("repeat_header")) %>% 
      column_spec(1, width = "7cm")
  }
}
```

```{r mindsetCNI.catMod-trends-tables, results='asis'}
# Moderator names
cat_mod_names <- c("family_home",  "mother_edu", "father_edu", "age_group") #"sex",

# Print all the tables
walk(cat_mod_names, function(var) {
  cat("\n\n")
  print(sig_groups1(mindsetCNI.CatMod_effects_trends, var, "Mindset CNI"))
  cat("\n\n")
})
```

For degrees of freedom, Kenward-Roger approximation was preferred, over Satterthwaite's approximation, as it provides adjusted degrees of freedom and adjusts the covariance matrix of the fixed effects, aiming for more accurate Type I error rates, especially in small samples/complex models.  


```{r fun.-cni-CatMod-effects, echo= T, eval=F}
#Explanation for function below
      #[which CNI-type]:
  #cni_profiles_data <- mindsetCNI_profiles1 [self.ctry_profiles,overallM_profiles] 
      #[which moderator]:
  # "sex","family_home","mother_edu","father_edu","age_group"    
  #Model: CNI <- Categorical moderator

#levels(factor(data2$father_edu)) #how many levels?
#choose(9, 2) #check for number of contrasts

#This version of the function is necessary for parallel processing! Moderators are varied. 

cni.CatMod_effects(mindsetCNI_profiles, "family_home")

cni.CatMod_effects <- function(cni_profiles_data, modtr_cat) {
  
  #consists of self,ctry and overall.M profiles
  joined_profiles <- pluck(cni_profiles_data, "self.ctry_profiles") %>%
  left_join(pluck(cni_profiles_data, "overallM_profiles"), by = "item")

  #right data format
  cni.modtr_data <- data2 %>% 
    #select moderator scales individual level (pID) scores 
    select(pID, all_of(modtr_cat)) %>% 
    pivot_longer(-pID, 
                 names_to = "modtr", #moderator name
                 values_to = "modtr_score") %>% # moderator score
    full_join(joined_profiles, by = c("pID"), relationship = "many-to-many")
  
  #1. CNI <- moderator
  cni.modtr_model <- cni.modtr_data %>%
      #cni ~ mod [linear]
      lmer(z_response ~ z_ctry_response * modtr_score + overall.M + (-1 + z_ctry_response | pID), data = .)
      
      #save results
  #2. model fit   
  #Deafult = Kenward-Roger Approximation
   model_fit <- Anova(cni.modtr_model, type = "III", test.statistic = "F") %>%  tidy()
   #3. contrasts
   trends <- emtrends(cni.modtr_model, pairwise ~ modtr_score,
         var = "z_ctry_response",
         adjust = "holm")

  
  return(lst(model_fit,trends))
}
```

```{r parallel-processing-catMods, echo = F, eval = F}
#This code chunk is representative of the 
# Hardware specifications: 12 cores, 62 GB RAM

# Load necessary libraries
library(furrr);library(purrr);library(tictoc)
library(car)
emm_options(pbkrtest.limit = 521388) #emtrends setting

# Set up cores
  plan(multisession, workers = availableCores() - 1)

tic()
# All categorical moderator variables
  var_names <- c("sex", "age_group" , "mother_edu","father_edu",
                 "family_home")

#checklist
#1. change the name of the object according to the CNI being used
#2. change the data_profiles object name
#3. save the object in Study 2
  
  #pty6

# Parallel execution using furrr
  pty6CNI.cat_effects<- future_map(var_names, function(var) {
    result <- cni.CatMod_effects(pty6CNI_profiles, var)
    return(result)
  }, .progress = TRUE) %>% 
    set_names(var_names)


# Reset to sequential processing
plan(sequential)
toc()

#object diagnostics:
  #library(pryr)
  #rm(globeExCNI.cat_effects)
  #object_size(fantcCNI.cat_effects)
  #object_size(globeExCNI.cat_effects$father_edu)
```

```{r save-cni.CatMod-models, echo = F, eval = F}
#checklist 
#1. change name of the object  
#2. DANGER: change name of the object being saved
#use the following to save each or collected chunks in the code above
save(pty6CNI.cat_effects,
     file = here("objects/Study2/pty6CNI.cat_effects.Rdata"))
```

```{r load-cni.CatMod-models, echo=F, results='hide'}
options(scipen = 999)

# Define a vector of file names
cni.catMod_object_names <- paste0(c(
  "ismCNI",
  "globeCNI",
  "globeExCNI",
  "fantcCNI",
  "mfCNI",
  "socAxCNI",
  "pty6CNI"), ".cat_effects.Rdata")

# Set file paths and set names
filepaths <- here("objects/Study2", cni.catMod_object_names) %>%
  set_names(nm = basename(.) %>% tools::file_path_sans_ext())

# Load all files
all_cni.catMod_effects <- purrr::map(filepaths, ~get(load(.)))

# Assign loaded objects to global environment - important!
purrr::pmap(.l = list(.x = names(all_cni.catMod_effects), .y = all_cni.catMod_effects), .f = ~assign(.x, .y, envir = .GlobalEnv))

# Verify that objects are now in the global environment
#map_lgl(names(all_cni.catMod_effects), ~exists(.x, envir = .GlobalEnv))
```



### Model fit

These 

```{r anova-cni.catMod_effects}
cat_var_names <- c("age_group" , "mother_edu","father_edu",
                 "family_home")#"sex", 

cat_fit_tbl <- \(cat_var){
  
  title_cap <- function(s){
   s %>%
    str_replace_all("_", " ") %>%
    str_to_sentence() %>%
    str_replace("edu", "Education")}
 
  
  map_dfr(all_cni.catMod_effects, 
        pluck, cat_var, "model_fit", 
        .id = "CNI_type") %>% 
    filter(!str_detect(tolower(term), "intercept")) %>% #distinct(term)
  mutate(term = case_when(
          term == "z_ctry_response" ~ "CNI",
        term == "modtr_score" ~ "Predictor",
        term == "overall.M" ~ "Overall Mean",
        grepl(":", term, fixed = TRUE) ~ "Interaction",
        TRUE ~ term
    ),
    stars = case_when(
    p.value < .001 ~ "***",
    p.value < .01 ~ "**",
    p.value < .05 ~ "*",
    TRUE ~ ""),
    statistic = sprintf("F(%d, %.0f) = %.2f%s", 
           df, Df.res, statistic, stars),
     CNI_type = case_when(
            CNI_type == "ismCNI.cat_effects" ~ "Isms CNI",
            CNI_type == "globeCNI.cat_effects" ~ "Globe CNI",
            CNI_type == "globeExCNI.cat_effects" ~ "Globe Extra CNI",
            CNI_type == "mfCNI.cat_effects" ~ "Moral Foundations CNI",
            CNI_type == "fantcCNI.cat_effects" ~ "Fanaticism CNI",
            CNI_type == "pty6CNI.cat_effects" ~ "Personality 6 CNI",
            CNI_type == "socAxCNI.cat_effects" ~ "Social Axioms CNI",
            TRUE ~ CNI_type)) %>% 
    select(CNI_type, term, statistic) %>% 
   pivot_wider(names_from = term, values_from = statistic) %>% 
     kable(booktabs = T,
           longtable = T,
           format = "latex",
        caption = paste0("ANOVA summary of ",  title_cap({{cat_var}}), " individual characteristic models")) %>% 
  kable_styling() %>% 
  column_spec(2, width = "3cm") %>% 
  column_spec(3, width = "3cm") %>% 
  column_spec(4, width = "3cm") %>% 
  column_spec(5, width = "3cm")
}
```

```{r walk-anova-cni.catMod_effects, results = 'asis', eval=TRUE, echo=FALSE}
#Define the categorical moderators
cat_mod_names <- c("family_home", "mother_edu", "father_edu", "age_group")

# Use walk to iterate over the categorical moderators
walk(cat_mod_names, function(var) {
  result <- cat_fit_tbl(var)
  print(result)
  cat("\n\n")  # Add some space between tables
})
```

For making model comparisons. 
Issues with running model fit for Mindset-CNI were encountered. The data was too large for `car::Anova` with `statistic = "F"` (tried with 23 cores and 120 GB RAM on Talapas); code kept crashing. As an alternative, chi square test comparing the H0(null model; no moderator) and H1(alternative model; with moderator) was computed for every moderator. `car::Anova` with `statistic = "Chisq"` is used to facilitate model comparison across all CNI models.

```{r cni.CatMod_AnovaChisq}
cni.CatMod_AnovaChisq <- function(cni_profiles_data, modtr_cat) {
  
  #consists of self,ctry and overall.M profiles
  joined_profiles <- 
    pluck(all_profiles, cni_profiles_data, "self.ctry_profiles") %>%
  left_join(pluck(all_profiles , cni_profiles_data, "overallM_profiles"), by = "item")

  #right data format
  cni.modtr_data <- data2 %>% 
    #select moderator scales individual level (pID) scores 
    select(pID, all_of(modtr_cat)) %>% 
    pivot_longer(-pID, 
                 names_to = "modtr", #moderator name
                 values_to = "modtr_score") %>% # moderator score
    full_join(joined_profiles, by = c("pID"), relationship = "many-to-many")
  
    #1. CNI <- moderator
  cni.modtr_model <- cni.modtr_data %>%
      #cni ~ mod [linear]
      lmer(z_response ~ z_ctry_response*modtr_score + overall.M + (-1 + z_ctry_response | pID), data = .)
      
      #save results
  #2. model fit   
  #Deafult = Kenward-Roger Approximation
   model_fit <- Anova(cni.modtr_model, type = "III", test.statistic = "Chisq") %>%  broom::tidy()
   
   return(model_fit)
}

#cni.CatMod_AnovaChisq("pty6CNI_profiles", "sex")

cni.CatMod_AnovaChisq_details <- expand_grid(
  cni = names(all_profiles), 
  modtr = c("sex", "age_group" , "mother_edu","father_edu",
                 "family_home"))
```


```{r DONT-RUN-cni.CatMod_AnovaChisq, echo = F, eval=FALSE}
#Hardware specifications:
# 16GB RAM, 8 cores

# Load libraries
library(furrr);library(purrr);library(tictoc);library(car); library(broom)

# Set up cores
  plan(multisession, workers = availableCores() - 1)

# Run the analysis
tic()
cni.cat_AnovaChisq_fit <- future_pmap(
  cni.CatMod_AnovaChisq_details,
  function(cni, modtr) {
    result <- cni.CatMod_AnovaChisq(cni, modtr)
    return(result)
  },
  .progress = TRUE
) %>% 
  set_names(with(cni.CatMod_AnovaChisq_details, paste(cni, modtr, sep = "_")))

# Reset to sequential processing
plan(sequential)
toc()

cni.cat_AnovaChisq_fit 
```

```{r save-cni.CatMod_AnovaChisq, echo = F, eval = F}
save(cni.cat_AnovaChisq_fit,
     file = here("objects/Study2/cni.cat_AnovaChisq_fit.Rdata"))
```

```{r load-cni.CatMod_AnovaChisq, echo = F, eval = T}
load("~/Desktop/CNI_Dissertation/objects/Study2/cni.cat_AnovaChisq_fit.Rdata")
```


```{r cat_fit.chisq_tbl}
cat_fit.chisq_tbl <- function(cat_var) {
  
  title_cap <- function(s) {
    s %>%
      str_replace_all("_", " ") %>%
      str_to_sentence() %>%
      str_replace("edu", "Education")
  }
 
bind_rows(cni.cat_AnovaChisq_fit, .id = "CNI_type") %>%
  separate(CNI_type, into = c("CNI_type", "profiles", "moderator"), sep = "_", extra = "merge") %>%
  filter(moderator == cat_var) %>% 
    select(-profiles, -moderator)%>% 
    filter(!str_detect(tolower(term), "intercept")) %>%
    mutate(
      term = case_when(
        term == "z_ctry_response" ~ "CNI",
        term == "modtr_score" ~ "Predictor",
        term == "overall.M" ~ "Overall Mean",
        grepl(":", term, fixed = TRUE) ~ "Interaction",
        TRUE ~ term),
      stars = case_when(
        p.value < .001 ~ "***",
        p.value < .01 ~ "**",
        p.value < .05 ~ "*",
        TRUE ~ ""
      ),
     statistic = sprintf("(%d) = %.2f%s", 
                          df, statistic, stars),
      CNI_type = case_when(
        CNI_type == "mindsetCNI" ~ "Mindset CNI",
        CNI_type == "ismCNI" ~ "Isms-Mindset CNI",
        CNI_type == "fantcCNI" ~ "Fanaticism-Mindset CNI",
        CNI_type == "globeCNI" ~ "Globe-Mindset CNI",
        CNI_type == "globeExCNI" ~ "Globe Extra-Mindset CNI",
        CNI_type == "mfCNI" ~ "Moral Foundations-Mindset CNI",
        CNI_type == "socAxCNI" ~ "Social Axioms-Mindset CNI",
        CNI_type == "pty6CNI" ~ "Personality 6 CNI",
        TRUE ~ CNI_type
      )) %>% 
    select(CNI_type, term, statistic) %>% 
    pivot_wider(names_from = term, values_from = statistic) %>% 
  kable(booktabs = T,
           longtable = T,
           format = "latex",
        caption = paste0("ANOVA summary of ",  title_cap({{cat_var}}), " individual characteristic models")) %>% 
  kable_styling() %>% 
  column_spec(2, width = "3cm") %>% 
  column_spec(3, width = "3cm") %>% 
  column_spec(4, width = "3cm") %>% 
  column_spec(5, width = "3cm")}
```

```{r walk-cat_fit.chisq_tbl, results = 'asis', eval=TRUE, echo=FALSE}
cat_var_names <- c("age_group" , "mother_edu","father_edu",
                 "family_home")#"sex",
# Use walk to iterate over the categorical moderators
walk(cat_var_names, function(var) {
  result <- cat_fit.chisq_tbl(var)
  print(result)
  cat("\n\n")  # Add some space between tables
})
```
### Marginal effects

#### Estimated slopes (trends) 

```{r emtrends-cni.catMod_effects}
cat_emtrends_tbl <- \(cat_var){
  title_cap <- function(s){
   s %>%
    str_replace_all("_", " ") %>%
    str_to_sentence() %>%
    str_replace("edu", "Education")}
  group_names <- c("Mindset CNI", "Isms-Mindset CNI", "Fanaticism-Mindset CNI", "Globe-Mindset CNI", "Globe Extra-Mindset CNI", "Moral Foundations-Mindset CNI", "Social Axioms-Mindset CNI", "Personality6 CNI")
  
 full_df <- 
   rbind(
 mindsetCNI.CatMod_effects_trends %>% 
       pluck(cat_var, "emtrends") %>% 
      as_tibble() %>% 
      mutate(CNI_type = "mindsetCNI.cat_effects", 
             .before = modtr_score), 
    map_df(all_cni.catMod_effects, 
      ~as_tibble(summary(pluck(.x, cat_var, "trends", "emtrends"))),
                 .id = "CNI_type"))  
    
  full_df %>%  
      mutate(CNI_type = case_when(
        CNI_type == "mindsetCNI.cat_effects" ~ "Mindset CNI",
    CNI_type == "ismCNI.cat_effects" ~ "Isms-Mindset CNI",
    CNI_type == "globeCNI.cat_effects" ~ "Globe-Mindset CNI",
    CNI_type == "globeExCNI.cat_effects" ~ "Globe Extra-Mindset CNI",
    CNI_type == "fantcCNI.cat_effects" ~ "Fanaticism-Mindset CNI",
    CNI_type == "mfCNI.cat_effects" ~ "Moral Foundations-Mindset CNI",
    CNI_type == "socAxCNI.cat_effects" ~ "Social Axioms-Mindset CNI",
    CNI_type == "pty6CNI.cat_effects" ~ "Personality6 CNI",
    TRUE ~ CNI_type)) %>% 
     select(-CNI_type, -df) %>% 
    mutate(across(where(is.numeric), printnum)) %>% 
     kable(booktabs = T,
           longtable = T,
           format = "latex",
            col.names = c("Group", "CNI", "SE", "Lower", "Upper"),
        caption = paste0("Expected CNI by ",  title_cap({{cat_var}}), ".")) %>% #
   kable_styling(latex_options = c("repeat_header", "longtable")) %>% 
   {reduce(seq_along(group_names), 
           .init = ., 
           ~ group_rows(.x, group_names[.y], n_distinct(full_df$modtr_score)*(.y-1)+1, n_distinct(full_df$modtr_score)*.y))} %>% 
  column_spec(1, width = "7.2cm") %>% 
    add_header_above(c(" " = 3, "95% CI" = 2))
}
```

```{r walk-emtrends-cni.catMod_effects, results = 'asis', echo=FALSE, eval=TRUE}
#| cache: true
#Define the categorical moderators
cat_mod_names <- c("family_home", "mother_edu", "father_edu", "age_group")

# Use walk to iterate over the categorical moderators
walk(cat_mod_names, function(var) {
  result <- cat_emtrends_tbl(var)
  print(result)
  cat("\n\n")  # Add some space between tables
})
```

```{r emtrends-cni.catMod-emtrends_plot}
cat_emtrends_plot <- \(cat_var){
  
   xtitle <- function(s){
     s %>%
    str_replace_all("_", " ") %>%
    str_to_sentence() %>%
    str_replace("edu", "Education")}
  
plot_data <-  rbind(
 mindsetCNI.CatMod_effects_trends %>% 
       pluck(cat_var, "emtrends") %>% 
      as_tibble() %>% 
      mutate(CNI_type = "mindsetCNI.cat_effects", 
             .before = modtr_score), 
    map_df(all_cni.catMod_effects, 
      ~as_tibble(summary(pluck(.x, cat_var, "trends", "emtrends"))),
                 .id = "CNI_type")) %>% 
     mutate(CNI_type = case_when(
        CNI_type == "mindsetCNI.cat_effects" ~ "Mindset CNI",
    CNI_type == "ismCNI.cat_effects" ~ "Isms-Mindset CNI",
    CNI_type == "globeCNI.cat_effects" ~ "Globe-Mindset CNI",
    CNI_type == "globeExCNI.cat_effects" ~ "Globe Extra-Mindset CNI",
    CNI_type == "fantcCNI.cat_effects" ~ "Fanaticism-Mindset CNI",
    CNI_type == "mfCNI.cat_effects" ~ "Moral Foundations-Mindset CNI",
    CNI_type == "socAxCNI.cat_effects" ~ "Social Axioms-Mindset CNI",
    CNI_type == "pty6CNI.cat_effects" ~ "Personality6 CNI",
    TRUE ~ CNI_type  # keep original if no match
  ))

# Create the plot
ggplot(plot_data, aes(x = modtr_score, y = z_ctry_response.trend, fill = modtr_score)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.2, position = position_dodge(0.9)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
   coord_flip()+
  facet_wrap(~ CNI_type, ncol = 2) +
  labs(x = xtitle({{cat_var}}), 
       y = "Estimated Marginal Trend",
      fill = "Levels") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_fill_brewer(palette = "Set3")

}

cat_emtrends_plot_details <- tibble(
        cat_mod = c("family_home", "mother_edu", "father_edu", "age_group")) %>% 
 mutate(cat_mod = map_chr(cat_mod, function(x) {
   x %>%
    str_replace_all("_", " ") %>%
    str_to_sentence() %>%
    str_replace("edu", "Education")}),
  caption = paste0("Expected CNI by ", cat_mod))
```

```{r walk-emtrends-cni.catMod-emtrends_plot, results = 'asis', echo=FALSE, eval=TRUE}
#| cache: true
#| fig-height: 12
#| fig-width: 10
#| out-width: "100%"
#| cap-location: bottom
#| fig-cap: !expr |
#|   cat_emtrends_plot_details %>%
#|     pull(caption)

cat_mod_names <- c("family_home", "mother_edu", "father_edu", "age_group")

# Use walk to iterate over the categorical moderators
walk(cat_mod_names, function(var) {
  result <- cat_emtrends_plot(var)
  print(result)
  cat("\n\n")  # Add some space between tables
})
```

#### Contrasts

```{r fun.-sig_groups2}
sig_groups2 <- function(CNI.cat_effects, var, cni_name, sig.only = FALSE) {
   # Extract the part of cni_name before the first period
  cni_name_cap <- str_extract(cni_name, "^[^.]+")
  
  #age_group -> "Age group"
  var_name_cap <- var %>%
    str_replace_all("_", " ") %>%
    str_to_title()
  
  trends <- CNI.cat_effects %>% 
    pluck(cni_name,var, "trends", "contrasts") %>% 

    as.data.frame()

if (sig.only) {
    trends <- filter(trends, p.value < .05)
    cap <- paste0("Significant differences in ", cni_name_cap, " by ", var_name_cap, ".")
  } else {
    cap <- paste0("Differences in ", cni_name_cap, " by ", var_name_cap, ".")
  }
  
  if (nrow(trends) > 0) {
    trends %>% 
      mutate(
        p.value = papaja::printp(p.value),
        across(where(is.numeric), printnum)) %>% 
      select(-df) %>% 
      kable(booktabs = T,
            caption = cap,
            longtable = T,
            format = "latex",
             col.names = c("Contrast", "Est", "SE", "Z", "p")) %>% 
      kable_styling(latex_options = c("repeat_header")) %>% 
      column_spec(1, width = "7.2cm")
  }
}

```

```{r cni.catMod_effects_tables, results = 'asis', echo=FALSE, eval=TRUE}
# categorical moderators
cat_mod_names  <- c("family_home", "mother_edu", "father_edu", "age_group")

# CNI names (adjust this list according to your needs)
cni_names <- names(all_cni.catMod_effects)

# Iterate over both cni_names and cat_mod_names 
walk(cni_names, function(cni) {
  walk(cat_mod_names , function(var) {
    result <- sig_groups2(all_cni.catMod_effects, var, cni)
    if (!is.null(result)) {
      print(result)
      cat("\n\n")  # Add some space between tables
    }
  })
})
```

## Tables - Contrasts( _p_ < .05)

```{r sig-only.catMod-trends-plots, results='asis', echo=FALSE, eval=TRUE}
#| cache: true
# Moderator names
cat_mod_names <- c("family_home",  "mother_edu", "father_edu", "age_group") #"sex",

#--Mindset CNI--#
# Print all the tables
walk(cat_mod_names, function(var) {
  cat("\n\n")
  print(sig_groups1(mindsetCNI.CatMod_effects_trends, var, "Mindset CNI", sig.only = TRUE))
  cat("\n\n")
})

#--others CNI's--#

# CNI names (adjust this list according to your needs)
cni_names <- names(all_cni.catMod_effects)

# Iterate over both cni_names and cat_mod_names 
walk(cni_names, function(cni) {
  walk(cat_mod_names , function(var) {
    result <- sig_groups2(all_cni.catMod_effects, var, cni, sig.only = TRUE)
    if (!is.null(result)) {
      print(result)
      cat("\n\n")  # Add some space between tables
    }
  })
})
```
